---
title: "Keyword landscape analysis - ahrefs"
author: ""
date: "Last updated on `r Sys.Date()`"
output:
  html_document:
    theme: paper
    highlight: kate
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: true
editor_options: 
  chunk_output_type: inline
---


<style>
.list-group-item.active, .list-group-item.active:hover, .list-group-item.active:focus {
  background-color: #00d188;
  border-color: #00d188;
}

body {
  font-family: montserrat;
  color: #444444;
  font-size: 14px;
}

h1 {
  font-weight: bold;
  font-size: 28px;
}

h1.title {
  font-size: 30px;
  color: #00d188;
}

h2 {
  font-size: 24px;
}

h3 {
  font-size: 18px;
}
</style>



```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = F, message = F, fig.path = "../plots/", cache = F, fig.showtext = TRUE, dpi = 700)

knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", small.mark = ",", scientific = F)
})

Sys.setlocale("LC_TIME", "C")
extrafont::loadfonts(device = "win")
```


```{r prep}
set.seed(2)

required_packages <- c("tidyverse", "magrittr", "DBI", "bigrquery", "arrow","glue", "vroom","janitor", "gt", "ggwordcloud", "readxl", "ggthemes", "hrbrthemes", "extrafont", "plotly", "scales", "stringr", "gganimate", "here", "tidytext", "sentimentr", "scales", "DT", "here", "sm", "mblm", "glue", "fs", "knitr", "rmdformats", "janitor", "urltools", "colorspace", "pdftools", "showtext", "pander", "ggridges", "spatstat", "broom", "arrow")
for(i in required_packages) { 
  if(!require(i, character.only = T)) {
    #  if package is not existing, install then load the package
    install.packages(i, dependencies = T)
  require(i, character.only = T)
  }
}

panderOptions('table.alignment.default', "left")

## quality of png's
dpi <- 750

## theme updates; please adjust to client´s website
#theme_set(ggthemes::theme_clean(base_size = 15))
theme_set(ggthemes::theme_clean(base_size = 15))
theme_update(plot.margin = margin(30, 30, 30, 30),
             plot.background = element_rect(color = "white",
                                            fill = "white"),
             plot.title = element_text(size = 20,
                                       face = "bold",
                                       lineheight = 1.05,
                                       hjust = .5,
                                       margin = margin(10, 0, 25, 0)),
             plot.title.position = "plot",
             plot.caption = element_text(color = "grey40",
                                         size = 9,
                                         margin = margin(20, 0, -20, 0)),
             plot.caption.position = "plot",
             axis.line.x = element_line(color = "black",
                                        size = .8),
             axis.line.y = element_line(color = "black",
                                        size = .8),
             axis.title.x = element_text(size = 16,
                                         face = "bold",
                                         margin = margin(t = 20)),
             axis.title.y = element_text(size = 16,
                                         face = "bold",
                                         margin = margin(r = 20)),
             axis.text = element_text(size = 11,
                                      color = "black",
                                      face = "bold"),
             axis.text.x = element_text(margin = margin(t = 10)),
             axis.text.y = element_text(margin = margin(r = 10)),
             axis.ticks = element_blank(),
             panel.grid.major.x = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.major.y = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.minor.x = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.minor.y = element_blank(),
             panel.spacing.x = unit(4, "lines"),
             panel.spacing.y = unit(2, "lines"),
             legend.position = "top",
             legend.title = element_text(family = "Montserrat",
                                         color = "black",
                                         size = 14,
                                         margin = margin(5, 0, 5, 0)),
             legend.text = element_text(family = "Montserrat",
                                        color = "black",
                                        size = 11,
                                        margin = margin(4.5, 4.5, 4.5, 4.5)),
             legend.background = element_rect(fill = NA,
                                              color = NA),
             legend.key = element_rect(color = NA, fill = NA),
             #legend.key.width = unit(5, "lines"),
             #legend.spacing.x = unit(.05, "pt"),
             #legend.spacing.y = unit(.55, "pt"),
             #legend.margin = margin(0, 0, 10, 0),
             strip.text = element_text(face = "bold",
                                       margin = margin(b = 10)))
## theme settings for flipped plots
theme_flip <-
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_line(size = .6,
                                          color = "#eaeaea"))
## theme settings for charts without y axis
theme_blank <- 
  theme(panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.line.y = element_blank(),
        axis.text.y = element_blank())

## numeric format for labels
num_format <- scales::format_format(big.mark = ",", small.mark = ",", scientific = F)
## main color backlinko
bl_col <- "#00d188"
bl_dark <- darken(bl_col, .3, space = "HLS")
```


# Read data

```{r}
df <- bind_rows(
    pmap_df(list(0:99), ~read_csv(glue("../proc_data/ahref/export_keywords_100_to_500/{.x}.csv"))) %>% 
        clean_names() %>% mutate(cat = "100-500"),
    pmap_df(list(0:99), ~read_csv(glue("../proc_data/ahref/export_keywords_500_to_1000/{.x}.csv"))) %>% 
        clean_names() %>% mutate(cat = "500-1000"),
    pmap_df(list(0:49), ~read_csv(glue("../proc_data/ahref/export_keywords_1000_to_10000/{.x}.csv"))) %>% 
        clean_names() %>% mutate(cat = "1000-10000"),
    pmap_df(list(0:33), ~read_csv(glue("../proc_data/ahref/export_keywords_10000_to_1000000000/{.x}.csv"))) %>% 
            clean_names() %>% mutate(cat = "10000+")
)
```


<br>

# Preamble


<br>

The volume looks weird. It doesn't follow the initial categories:

```{r}
df %>% drop_na(volume) %>% 
    group_by(cat) %>% 
    summarise(
        n = n(),
        mean = mean(volume),
        median = median(volume),
        max = max(volume),
        min = min(volume)
        ) %>% 
    arrange(median) %>% 
    pander()
```

Let's look at some of the searches that had a low search volume in the initial data set:

```{r}
df %>% filter(cat == "100-500", volume > 10000) %>% 
    select(keyword, volume) %>% 
    head(5) %>% 
    pander()
```

This doesn't looks like low volume words. And indeed they were not in the original data sets for 100-500 volume. I'm not sure how they came in.

This removes those keywords that were not in the same category in the data samples I created:


```{r}
df_orig <- bind_rows(
    pmap_df(list(0:99), ~read_csv(glue("../raw_data/keywords_100_to_500/{.x}.txt"), col_names = c("keyword"))) %>% 
        clean_names() %>% select(keyword) %>% mutate(cat = "100-500"),
    pmap_df(list(0:99), ~read_csv(glue("../raw_data/keywords_500_to_1000/{.x}.txt"), col_names = c("keyword"))) %>% 
        clean_names() %>% mutate(cat = "500-1000"),
    pmap_df(list(0:99), ~read_csv(glue("../raw_data/keywords_1000_to_10000/{.x}.txt"), col_names = c("keyword"))) %>% 
        clean_names() %>% mutate(cat = "1000-10000"),
    pmap_df(list(0:99), ~read_csv(glue("../raw_data/keywords_10000_to_1000000000/{.x}.txt"), col_names = c("keyword"))) %>% 
            clean_names() %>% mutate(cat = "10000+")
)
```

```{r}
df %<>% inner_join(df_orig, by = c("cat", "keyword"))
```

There are still ~2.5 million rows left:

```{r}
tibble("Number of rows" = format(df %>% nrow(), big.mark = ",")) %>% 
  pander()
```




Another issue is that of the representativeness of the samples. Keywords with less than 100 volume are not even represented. And the othe rvolumes are represented at skewed ratios. This makes a large difference, especially if we look at stats based on search instead of based on volume.

To me, it still makes most sense to look at it based on volume. But you've been quite clear that this is not what we want. Still, it seems wrong to me to use this unrepresentative dataset, and report things such as mean. That will fully depend on how we happened to create the samples. Since most of searches have low volume, removing those with volume below 100 makes a huge difference.

So, for analyses where this is important, I will perform them in three different ways.

1. Using the samples here directly

2. Using the samples here, but scaled so that they are representative of the original data set. (Except that < 100 volume is removed.)

3. Using the scaled samples, and also go by volume instead of count.

As we can see, these three approaches give quite different results.

```{r}
length_keyword_files <- function(min, max){
  sql <- glue("SELECT count(*) as `count`
          FROM `dataforseo-bigquery.dataforseo_data.keyword_data` 
          WHERE location = 2840 
          AND keyword_info_search_volume >= {min}
          AND keyword_info_search_volume < {max}")
  tb <- bq_project_query("dataforseo-bigquery", sql)
  df <- bq_table_download(tb) %>% mutate(min = min, max = max)
}

scaling <- map2_df(c(0, 100, 500, 1000, 10000), c(100, 500, 1000, 10000, 1000000000), length_keyword_files) %>% 
    mutate(factor = count / 1000000) %>% relocate(min, max)

scaling %>% pander()
```


<br>


```{r}
df %<>% mutate(
  difficulty_cat = case_when(
    difficulty <= 10 ~ "Easy\n(0-10)",
    between(difficulty, 11, 30) ~ "Medium\n(11-30)",
    between(difficulty, 31, 70) ~ "Hard\n(31-70)",
    between(difficulty, 71, 100) ~ "Super hard\n(71-100)"
  )) %>% 
  mutate(difficulty_cat = factor(difficulty_cat, levels = c("Easy\n(0-10)", "Medium\n(11-30)", "Hard\n(31-70)", "Super hard\n(71-100)"))) %>% 
  mutate(log_volume = log10(volume))

dfs <- df %>% sample_n(20000) 

rdf <- bind_rows(
  df %>% filter(between(volume, 100, 500)) %>% 
    sample_n(scaling %>% filter(min == 100) %>% pull(factor) * 2000),
  df %>% filter(between(volume, 100, 500)) %>% 
    sample_n(scaling %>% filter(min == 500) %>% pull(factor) * 2000),
  df %>% filter(between(volume, 1000, 10000)) %>% 
    sample_n(scaling %>% filter(min == 1000) %>% pull(factor) * 2000),
  df %>% filter(between(volume, 10000, 1000000000)) %>% 
    sample_n(scaling %>% filter(min == 10000) %>% pull(factor) * 2000)
)
```

```{r}
df %>% write_feather("../proc_data/ahref/ahref.f")
rdf %>% write_feather("../proc_data/ahref/r_ahref.f")
```


