---
title: "Stopwords"
author: ""
date: "Last updated on `r Sys.Date()`"
output:
  html_document:
    theme: paper
    highlight: kate
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: true
editor_options: 
  chunk_output_type: inline
---


<style>
.list-group-item.active, .list-group-item.active:hover, .list-group-item.active:focus {
  background-color: #00d188;
  border-color: #00d188;
}

body {
  font-family: montserrat;
  color: #444444;
  font-size: 14px;
}

h1 {
  font-weight: bold;
  font-size: 28px;
}

h1.title {
  font-size: 30px;
  color: #00d188;
}

h2 {
  font-size: 24px;
}

h3 {
  font-size: 18px;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = F, message = F, fig.path = "../plots/1611/", cache = F, fig.showtext = TRUE, dpi = 700)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", small.mark = ",", scientific = F)
})
Sys.setlocale("LC_TIME", "C")
extrafont::loadfonts(device = "win")
```



```{r prep}
set.seed(1)
required_packages <- c("tidyverse", "magrittr", "DBI", "bigrquery", "arrow","glue", "vroom","janitor", "gt", "ggwordcloud", "readxl", "ggthemes", "hrbrthemes", "extrafont", "plotly", "scales", "stringr", "gganimate", "here", "tidytext", "sentimentr", "scales", "DT", "here", "sm", "mblm", "glue", "fs", "knitr", "rmdformats", "janitor", "urltools", "colorspace", "pdftools", "showtext", "pander", "wordcloud2", "stopwords", "magicfor", "gapminder", "ggridges")
for(i in required_packages) { 
  if(!require(i, character.only = T)) {
    #  if package is not existing, install then load the package
    install.packages(i, dependencies = T)
  require(i, character.only = T)
  }
}
panderOptions('table.alignment.default', "left")
## quality of png's
dpi <- 750
## theme updates; please adjust to client´s website
#theme_set(ggthemes::theme_clean(base_size = 15))
theme_set(ggthemes::theme_clean(base_size = 15, base_family = "Montserrat"))
theme_update(plot.margin = margin(30, 30, 30, 30),
             plot.background = element_rect(color = "white",
                                            fill = "white"),
             plot.title = element_text(size = 20,
                                       face = "bold",
                                       lineheight = 1.05,
                                       hjust = .5,
                                       margin = margin(10, 0, 25, 0)),
             plot.title.position = "plot",
             plot.caption = element_text(color = "grey40",
                                         size = 9,
                                         margin = margin(20, 0, -20, 0)),
             plot.caption.position = "plot",
             axis.line.x = element_line(color = "black",
                                        size = .8),
             axis.line.y = element_line(color = "black",
                                        size = .8),
             axis.title.x = element_text(size = 16,
                                         face = "bold",
                                         margin = margin(t = 20)),
             axis.title.y = element_text(size = 16,
                                         face = "bold",
                                         margin = margin(r = 20)),
             axis.text = element_text(size = 11,
                                      color = "black",
                                      face = "bold"),
             axis.text.x = element_text(margin = margin(t = 10)),
             axis.text.y = element_text(margin = margin(r = 10)),
             axis.ticks = element_blank(),
             panel.grid.major.x = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.major.y = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.minor.x = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.minor.y = element_blank(),
             panel.spacing.x = unit(4, "lines"),
             panel.spacing.y = unit(2, "lines"),
             legend.position = "top",
             legend.title = element_text(family = "Montserrat",
                                         color = "black",
                                         size = 14,
                                         margin = margin(5, 0, 5, 0)),
             legend.text = element_text(family = "Montserrat",
                                        color = "black",
                                        size = 11,
                                        margin = margin(4.5, 4.5, 4.5, 4.5)),
             legend.background = element_rect(fill = NA,
                                              color = NA),
             legend.key = element_rect(color = NA, fill = NA),
             #legend.key.width = unit(5, "lines"),
             #legend.spacing.x = unit(.05, "pt"),
             #legend.spacing.y = unit(.55, "pt"),
             #legend.margin = margin(0, 0, 10, 0),
             strip.text = element_text(face = "bold",
                                       margin = margin(b = 10)))
## theme settings for flipped plots
theme_flip <-
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_line(size = .6,
                                          color = "#eaeaea"))
## theme settings for charts without y axis
theme_blank <- 
  theme(panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.line.y = element_blank(),
        axis.text.y = element_blank())

## numeric format for labels
num_format <- scales::format_format(big.mark = ",", small.mark = ",", scientific = F)
## main color backlinko
bl_col <- "#00d188"
bl_dark <- darken(bl_col, .3, space = "HLS")
```



```{r}
overview <- read_csv("../proc_data/overview.csv")

con <- dbConnect(
    bigrquery::bigquery(),
    project = "dataforseo-bigquery",
    billing = "dataforseo-bigquery"
)
```

```{r}
length_keyword_files <- function(min, max){
  sql <- glue("SELECT count(*) as `count`
          FROM `dataforseo-bigquery.dataforseo_data.keyword_data` 
          WHERE location = 2840 
          AND keyword_info_search_volume >= {min}
          AND keyword_info_search_volume < {max}")
  tb <- bq_project_query("dataforseo-bigquery", sql)
  df <- bq_table_download(tb) %>% mutate(min = min, max = max)
}

scaling <- map2_df(c(0, 100, 500, 1000, 10000), c(100, 500, 1000, 10000, 1000000000), length_keyword_files) %>% 
    mutate(factor = count / 1000000) %>% relocate(min, max)

scaling %>% pander()
```

```{r}
df <- read_feather("../proc_data/ahref/ahref.f")
dfs <- sample_n(df, 20000)

rdf <- bind_rows(
  df %>% filter(between(volume, 100, 500)) %>% 
    sample_n(scaling %>% filter(min == 100) %>% pull(factor) * 2000),
  df %>% filter(between(volume, 100, 500)) %>% 
    sample_n(scaling %>% filter(min == 500) %>% pull(factor) * 2000),
  df %>% filter(between(volume, 1000, 10000)) %>% 
    sample_n(scaling %>% filter(min == 1000) %>% pull(factor) * 2000),
  df %>% filter(between(volume, 10000, 1000000000)) %>% 
    sample_n(scaling %>% filter(min == 10000) %>% pull(factor) * 2000)
)
```




Proportion of search features without SERP:

```{r}
rdf %>% filter(is.na(serp_features)) %$% sum(volume) / 
    rdf %$% sum(volume)
```


# SERP features

Note there are (at least) two additional SERP feature types, knowledge panel and videos, for which the sample size is too small to be included.

```{r}
dff <- dfs %>% 
  select(keyword, volume, clicks, cpc, serp_features, cps) %>% 
  separate_rows(serp_features, sep = ",") %>% 
  mutate(serp_features = ifelse(is.na(serp_features), "(None)", serp_features)) %>% 
  filter(!(serp_features %in% c("Videos", "Knowledge panel")))

nones <- dff %>% filter(serp_features == "(None)")

dffn <- dff %>% group_by(keyword) %>% 
  summarise(n_serp = n()) %>% 
  mutate(n_serp = ifelse(keyword %in% nones$keyword, 0, n_serp)) %>% 
  mutate(n_serp = ifelse(n_serp >= 6, "6+", as.character(n_serp))) %>% 
  mutate(n_serp = factor(n_serp, levels = c("0", "1", "2", "3", "4", "5", "6+")))

dffn <- left_join(dffn, dfs, by = "keyword")
```



In sample:


```{r serp_presence_orig, fig.height = 6.5, fig.width = 10}
dff %>% group_by(serp_features) %>% 
  summarise(prop = n() / nrow(dfs)) %>% 
  ggplot(aes(y = reorder(serp_features, prop), x = prop)) +
  geom_bar(stat = "identity", fill = bl_dark, width = 0.65) +
  scale_x_continuous(labels = scales::label_percent(accuracy = 1), expand = c(0, 0)) +
  theme(panel.grid.minor.x = element_blank(), 
        panel.grid.major.y = element_blank(), 
        axis.line.y = element_blank()) +
  labs(y = "SERP feature", x = NULL, title = "Presence of SERP features")#+
  #ggsave(here::here("plots", "reworked", "serp_features.pdf"),
  #       width = 10, height = 6.5, device = cairo_pdf)
```

```{r}
rdff <- rdf %>% 
  select(keyword, volume, clicks, cpc, serp_features, cps) %>% 
  separate_rows(serp_features, sep = ",") %>% 
  mutate(serp_features = ifelse(is.na(serp_features), "(None)", serp_features)) %>% 
  filter(!(serp_features %in% c("Videos", "Knowledge panel")))

nones <- rdff %>% filter(serp_features == "(None)")

rdffn <- rdff %>% group_by(keyword) %>% 
  summarise(n_serp = n()) %>% 
  mutate(n_serp = ifelse(keyword %in% nones$keyword, 0, n_serp)) %>% 
  mutate(n_serp = ifelse(n_serp >= 6, "6+", as.character(n_serp))) %>% 
  mutate(n_serp = factor(n_serp, levels = c("0", "1", "2", "3", "4", "5", "6+")))

rdffn <- left_join(dffn %>% select(keyword, n_serp), dfs, by = "keyword")
```

Representative:

```{r serp_presence_repr, fig.height = 6.5, fig.width = 10}
rdff %>% group_by(serp_features) %>% 
  summarise(prop = n() / nrow(rdff)) %>% 
  ggplot(aes(y = reorder(serp_features, prop), x = prop)) +
  geom_bar(stat = "identity", fill = bl_dark, width = 0.65) +
  scale_x_continuous(labels = scales::label_percent(accuracy = 1), expand = c(0, 0),
                     limits = c(0, .2)) +
  theme(panel.grid.minor.x = element_blank(), 
        panel.grid.major.y = element_blank(), 
        axis.line.y = element_blank()) +
  labs(y = "SERP feature", x = NULL, title = "Presence of SERP features")# +
  #ggsave(here::here("plots", "reworked", "serp_features.pdf"),
  #       width = 10, height = 6.5, device = cairo_pdf)
```

By volume:

```{r serp_presence_volume, fig.height = 5, fig.width = 7}
rdff %>% group_by(serp_features) %>% 
  summarise(prop = sum(volume) / sum(rdff$volume)) %>% 
  ggplot(aes(y = reorder(serp_features, prop), x = prop)) +
  geom_bar(stat = "identity", fill = "turquoise4", color = "black", width = 0.8) +
  scale_x_continuous(labels = scales::percent) +
  labs(y = "SERP feature", x = NULL, title = "Presence of SERP features")
```

In sample:


```{r serp_presence_n_orig}
dffn %>% group_by(n_serp) %>%
  summarise(n = n() / nrow(dffn)) %>% 
  ggplot(aes(x = n_serp, y = n)) +
  geom_bar(stat = "identity", fill = "turquoise4", color = "black", width = 0.8) +
  labs(x = "Number of serp features", y = NULL, title = "Distribution of SERP features") +
  scale_y_continuous(labels = scales::percent)
```

By volume:

```{r serp_presence_n_volume}
rdffn %>% group_by(n_serp) %>%
  summarise(prop = sum(volume) / sum(rdff$volume)) %>% 
  ggplot(aes(x = n_serp, y = prop)) +
  geom_bar(stat = "identity", fill = "turquoise4", color = "black", width = 0.8) +
  labs(x = "Number of serp features", y = NULL, title = "Distribution of SERP features") +
  scale_y_continuous(labels = scales::percent)
```



The knowledge card has a huge effect in reducing the cps, while the other SERP features have limited effect. Searches with the Shopping results SERP feature have higher cps on average.

```{r serp_cps, fig.width = 10, fig.height = 7.5}
order <- dff %>% 
  group_by(serp_features) %>%
  summarise(mean_cps = mean(cps, na.rm = T)) %>% 
  arrange(mean_cps) %>% 
  pull(serp_features)

  
dff %>% 
  mutate(serp_features = factor(serp_features, levels = order)) %>% 
  ggplot(aes(y = serp_features, x = cps)) +
  stat_density_ridges(fill = colorspace::desaturate(bl_col, .2), color = bl_dark, alpha = .7, size = 1) +
  scale_x_continuous(expand = c(0, 0)) +
  coord_cartesian(clip = "off") +
  labs(x = "Clicks per search", y = "SERP feature", title = "SERP features and clicks per search") +
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.x = element_blank())# +
  #ggsave(here::here("plots", "reworked", "serp_cps.pdf"),
  #       width = 10, height = 7.5, device = cairo_pdf)
```

```{r}
dff %>% group_by(serp_features) %>% 
    summarise(m = mean(cpc, na.rm = T)) %>% 
    arrange(m)
```




```{r serp_volume_ridge}
order <- dff %>% 
  group_by(serp_features) %>%
  summarise(mean_volume = mean(volume, na.rm = T)) %>% 
  arrange(mean_volume) %>% 
  pull(serp_features)

  
dff %>% 
  mutate(serp_features = factor(serp_features, levels = order)) %>% 
  ggplot(aes(y = serp_features, x = volume)) +
  scale_x_log10(labels = comma) +
  stat_density_ridges(fill = "turquoise4", color = "black") +
  labs(y = "SERP feature", title = "SERP features and cps")

  
dff %>% 
  mutate(serp_features = factor(serp_features, levels = order)) %>% 
  ggplot(aes(y = serp_features, x = volume)) +
  stat_density_ridges(fill = colorspace::desaturate(bl_col, .2), color = bl_dark, alpha = .7, size = 1) +
  scale_x_log10(labels = comma) +
  coord_cartesian(clip = "off") +
  labs(x = "Volume", y = "SERP feature", title = "SERP features and volume") +
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.x = element_blank())# +
  #ggsave(here::here("plots", "reworked", "serp_volume.pdf"),
  #       width = 10, height = 7.5, device = cairo_pdf)
```


Low difficulty keywords have fewer SERP features 

```{r, serp_difficulty_boxplot, fig.height = 6.5, fig.width = 10}
rdffn %>% mutate(n_serp = as.numeric(n_serp)) %>% 
  drop_na(difficulty_cat) %>% 
  ggplot(aes(x = difficulty_cat, y = n_serp)) +
  geom_boxplot(color = bl_dark, fill = "grey92", size = .7, width = .7) +
  labs(x = "Difficulty", y = "SERP features", title = "Difficulty and number of SERP features")# +
  #ggsave(here::here("plots", "reworked", "serp_difficulty_box.pdf"),
  #       width = 10, height = 6.5, device = cairo_pdf)
```


```{r serp_difficulty_n, fig.width = 10, fig.height = 6.5}
rdffn %>% group_by(n_serp) %>%
  summarise(difficulty = mean(difficulty, na.rm = T)) %>% 
  ggplot(aes(x = n_serp, y = difficulty)) +
  geom_bar(stat = "identity", fill = bl_dark, color = "black", width = 0.8) +
  geom_text(aes(label = format(round(difficulty, 1), scientific = FALSE)),
            nudge_y = .7, family = "Montserrat", fontface = "bold", color = "grey40") +
  labs(x = "Number of SERP features", title = "Number of SERP features and mean difficulty", y = "Difficulty") +
  coord_cartesian(clip = "off") +
  scale_y_continuous(expand = c(.001, .001)) +
  theme(panel.grid.major.x = element_blank())# +
  #ggsave(here::here("plots", "reworked", "serp_mean_difficulty.pdf"),
  #       width = 10, height = 6.5, device = cairo_pdf)
```

```{r serp_pairs, fiog.width = 10, fig.height = 5}
find_pairs <-  function(){
  rs <- rdff %>% filter(serp_features != "(None)") %>% 
    sample_n(20000)
  kw <- rs %>% distinct(keyword) %>% pull(keyword)
  
  get_table <- function(k){
    a <- rs %>% filter(keyword == k, serp_features != "(None)")
    crossing(v1 = a$serp_features, v2= a$serp_features) %>% filter(v1 < v2)
  }
  
  pairs <- map_dfr(kw, get_table) %>% 
    group_by(v1, v2) %>% 
    summarise(n = n())
  
  pairs %>% write_csv("../proc_data/serp_pairs.csv")
}

pairs <- read_csv("../proc_data/serp_pairs.csv") %>% 
  mutate(n = n / sum(n))

pairs %>% 
  arrange(desc(n)) %>%
  head(10) %>% 
  mutate(pair = glue("{v1} & {v2}")) %>% 
  ggplot(aes(y = reorder(pair, n), x = n)) +
  geom_bar(stat = "identity", fill = bl_dark, width = 0.65) +
  labs(x = NULL, y = "SERP feature pair", title = "Most common SERP feature pairings") +
  scale_x_continuous(labels = scales::label_percent(accuracy = .1), 
                     breaks = seq(0, .15, by = .025), expand = c(0, 0), limits = c(0, .15)) +
  theme(panel.grid.minor.x = element_blank(), 
        panel.grid.major.y = element_blank(), 
        axis.line.y = element_blank())# +
  #ggsave(here::here("plots", "reworked", "serp_pairings.pdf"),
  #       width = 10, height = 5, device = cairo_pdf)
```


Definition SERP feautres: A SERP feature is any result on a Google Search Engine Results Page (SERP) that is not a traditional organic result. The most common SERP Features are: Rich Snippets which add a visual layer to an existing result (e.g., review stars for product ratings).

!!!D: after the 3rd, may make sense to check if there is anything interesting on relationship between keyword category and SERP features. 

Some definitions:

The Clicks column shows exactly how many times per month people tend to click any pages when googling this keyword. Some searches result in a lot of clicks, while other high search volume keywords may not bring in as much traffic from search due to the low number of clicks.

The keyword "chauffeur" has a high search volume of 67,000 searches per month. Yet that volume only resulted in 13,406 clicks. One probable reason could be that Google already gave what people wanted instantly - and there was no need to click on the search results.

!!!D: CPS column definition 

The CPS (Click per Search) shows an average number of clicks for all searches. It is basically a correlation between the Clicks metric and the Search Volume of the keyword. 

In the example given, people search for "wow chauffeur" less frequently than "chauffeur", yet the keyword has more Clicks than Searches. 

Further investigation reveals that the word "wow" actually stands for "World of Warcraft", and apparently, people are looking for information on how to summon a "chauffeur" in the game. That makes for a completely different search intent. 

And this is why we have the CPS metric. 

The higher the CPS (i.e people clicking on a few links to satisfy their search query) -- the more chances that you'll get some traffic even if you're not ranking #1 for that search query. 

More info: https://help.ahrefs.com/en/articles/624151-what-does-clicks-stand-for-in-keywords-explorer 


<br>