---
title: "Stopwords"
author: ""
date: "Last updated on `r Sys.Date()`"
output:
  html_document:
    theme: paper
    highlight: kate
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: true
editor_options: 
  chunk_output_type: inline
---


<style>
.list-group-item.active, .list-group-item.active:hover, .list-group-item.active:focus {
  background-color: #00d188;
  border-color: #00d188;
}

body {
  font-family: montserrat;
  color: #444444;
  font-size: 14px;
}

h1 {
  font-weight: bold;
  font-size: 28px;
}

h1.title {
  font-size: 30px;
  color: #00d188;
}

h2 {
  font-size: 24px;
}

h3 {
  font-size: 18px;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = F, message = F, fig.path = "../plots/1611/", cache = F, fig.showtext = TRUE, dpi = 700)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", small.mark = ",", scientific = F)
})
Sys.setlocale("LC_TIME", "C")
extrafont::loadfonts(device = "win")
```



```{r prep}
set.seed(1)
required_packages <- c("tidyverse", "magrittr", "DBI", "bigrquery", "arrow","glue", "vroom","janitor", "gt", "ggwordcloud", "readxl", "ggthemes", "hrbrthemes", "extrafont", "plotly", "scales", "stringr", "gganimate", "here", "tidytext", "sentimentr", "scales", "DT", "here", "sm", "mblm", "glue", "fs", "knitr", "rmdformats", "janitor", "urltools", "colorspace", "pdftools", "showtext", "pander", "wordcloud2", "stopwords", "magicfor", "gapminder")
for(i in required_packages) { 
  if(!require(i, character.only = T)) {
    #  if package is not existing, install then load the package
    install.packages(i, dependencies = T)
  require(i, character.only = T)
  }
}
panderOptions('table.alignment.default', "left")
## quality of png's
dpi <- 750
## theme updates; please adjust to client´s website
#theme_set(ggthemes::theme_clean(base_size = 15))
theme_set(ggthemes::theme_clean(base_size = 15, base_family = "Montserrat"))
theme_update(plot.margin = margin(30, 30, 30, 30),
             plot.background = element_rect(color = "white",
                                            fill = "white"),
             plot.title = element_text(size = 20,
                                       face = "bold",
                                       lineheight = 1.05,
                                       hjust = .5,
                                       margin = margin(10, 0, 25, 0)),
             plot.title.position = "plot",
             plot.caption = element_text(color = "grey40",
                                         size = 9,
                                         margin = margin(20, 0, -20, 0)),
             plot.caption.position = "plot",
             axis.line.x = element_line(color = "black",
                                        size = .8),
             axis.line.y = element_line(color = "black",
                                        size = .8),
             axis.title.x = element_text(size = 16,
                                         face = "bold",
                                         margin = margin(t = 20)),
             axis.title.y = element_text(size = 16,
                                         face = "bold",
                                         margin = margin(r = 20)),
             axis.text = element_text(size = 11,
                                      color = "black",
                                      face = "bold"),
             axis.text.x = element_text(margin = margin(t = 10)),
             axis.text.y = element_text(margin = margin(r = 10)),
             axis.ticks = element_blank(),
             panel.grid.major.x = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.major.y = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.minor.x = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.minor.y = element_blank(),
             panel.spacing.x = unit(4, "lines"),
             panel.spacing.y = unit(2, "lines"),
             legend.position = "top",
             legend.title = element_text(family = "Montserrat",
                                         color = "black",
                                         size = 14,
                                         margin = margin(5, 0, 5, 0)),
             legend.text = element_text(family = "Montserrat",
                                        color = "black",
                                        size = 11,
                                        margin = margin(4.5, 4.5, 4.5, 4.5)),
             legend.background = element_rect(fill = NA,
                                              color = NA),
             legend.key = element_rect(color = NA, fill = NA),
             #legend.key.width = unit(5, "lines"),
             #legend.spacing.x = unit(.05, "pt"),
             #legend.spacing.y = unit(.55, "pt"),
             #legend.margin = margin(0, 0, 10, 0),
             strip.text = element_text(face = "bold",
                                       margin = margin(b = 10)))
## theme settings for flipped plots
theme_flip <-
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_line(size = .6,
                                          color = "#eaeaea"))
## theme settings for charts without y axis
theme_blank <- 
  theme(panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.line.y = element_blank(),
        axis.text.y = element_blank())

## numeric format for labels
num_format <- scales::format_format(big.mark = ",", small.mark = ",", scientific = F)
## main color backlinko
bl_col <- "#00d188"
bl_dark <- darken(bl_col, .3, space = "HLS")
```




```{r}
overview <- read_csv("../proc_data/overview.csv")

con <- dbConnect(
    bigrquery::bigquery(),
    project = "dataforseo-bigquery",
    billing = "dataforseo-bigquery"
)
```





# Stopwords

```{r stopwords_count, fig.height = 6, fig.width = 6}
stopword_list <- tibble(stopword = stopwords::stopwords(language = "en")) %>% 
  mutate(stopword = str_remove(stopword, "'")) %>% 
  filter(!(stopword %in% c("shed", "wed", "ill", "hell", "shell")))
get_stopwords_counts <- function(){
  stopwords <- tribble(~stopword, ~n)
    for (word in stopword_list$stopword){
      print(word)
      sql <- glue(
        "SELECT COUNT(keyword_info_search_volume) AS stopword_count
         FROM `dataforseo-bigquery.dataforseo_data.keyword_data`
         WHERE location = 2840 
         AND keyword_info_search_volume > 0
         AND keyword like '% {word} %' OR keyword like '{word} %' OR keyword like '% {word}'")
      tb <- bq_project_query("dataforseo-bigquery", sql)
    
      df <- bq_table_download(tb) 
      stopwords %<>% add_row(stopword = word, n = df$stopword_count)
    }
    
    write_csv(stopwords, "../proc_data/stopwords.csv")
}
#get_stopwords_counts()
stopwords <- read_csv("../proc_data/stopwords.csv")
stopwords %>% mutate(prop = n / overview$count) %>%
  arrange(desc(prop)) %>% 
  head(10) %>% 
  ggplot(aes(x = reorder(stopword, prop), y = prop)) +
  geom_bar(stat = "identity", color = "black", fill = "turquoise4", width = 0.7) +
  scale_y_continuous(labels = scales::percent, expand = c(0,0), limits = c(0, 0.085)) +
  labs(x = NULL, y = NULL, title = "Searches with specific stopwords") +
  coord_flip()
```



!!!D: the graph is not that insightful. Please make the wordcloud a bit more readable and visually appealing. Feel to add more than 25 words. 




```{r wordcloud, fig.width = 10, fig.height = 7.5}
s2 <- stopwords %>% mutate(n = sqrt(n)) %>% arrange(-n)

#wordcloud2(s2, size = 0.6, gridSize = 15, minSize = 10,
#           fontFamily = "Montserrat", color = bl_col)

ggplot(s2, aes(label = stopword, size = n, color = n)) +
    geom_text_wordcloud(
      family = "Montserrat",
      fontface = "bold",
      shape = "circle",
      grid_margin = 2.5,
      seed = 1
    ) +
    #scale_color_gradient(low = "grey85", high = bl_dark) +
    scico::scale_color_scico(palette = "batlow", direction = -1) +
    scale_size_area(max_size = 25) +
    theme_void()

ggsave(here::here("plots", "reworked", "stopwords_cloud_colors.png"),
       width = 10, height = 7.5)
```
