---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

---
title: "Keyword landscape analysis"
author: ""
date: "Last updated on `r Sys.Date()`"
output:
  html_document:
    theme: paper
    highlight: kate
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: true
editor_options: 
  chunk_output_type: inline
---


<style>
.list-group-item.active, .list-group-item.active:hover, .list-group-item.active:focus {
  background-color: #00d188;
  border-color: #00d188;
}

body {
  font-family: montserrat;
  color: #444444;
  font-size: 14px;
}

h1 {
  font-weight: bold;
  font-size: 28px;
}

h1.title {
  font-size: 30px;
  color: #00d188;
}

h2 {
  font-size: 24px;
}

h3 {
  font-size: 18px;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = F, message = F, fig.path = "../plots/1611/", cache = F, fig.showtext = TRUE, dpi = 700)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", small.mark = ",", scientific = F)
})
Sys.setlocale("LC_TIME", "C")
extrafont::loadfonts(device = "win")
```



```{r prep}
set.seed(1)
required_packages <- c("tidyverse", "magrittr", "DBI", "bigrquery", "arrow","glue", "vroom","janitor", "gt", "ggwordcloud", "readxl", "ggthemes", "hrbrthemes", "extrafont", "plotly", "scales", "stringr", "gganimate", "here", "tidytext", "sentimentr", "scales", "DT", "here", "sm", "mblm", "glue", "fs", "knitr", "rmdformats", "janitor", "urltools", "colorspace", "pdftools", "showtext", "pander", "wordcloud2", "stopwords", "magicfor", "gapminder", "spatstat")
for(i in required_packages) { 
  if(!require(i, character.only = T)) {
    #  if package is not existing, install then load the package
    install.packages(i, dependencies = T)
  require(i, character.only = T)
  }
}
panderOptions('table.alignment.default', "left")
## quality of png's
dpi <- 750
## theme updates; please adjust to client´s website
#theme_set(ggthemes::theme_clean(base_size = 15))
theme_set(ggthemes::theme_clean(base_size = 15, base_family = "Montserrat"))
theme_update(plot.margin = margin(30, 30, 30, 30),
             plot.background = element_rect(color = "white",
                                            fill = "white"),
             plot.title = element_text(size = 20,
                                       face = "bold",
                                       lineheight = 1.05,
                                       hjust = .5,
                                       margin = margin(10, 0, 25, 0)),
             plot.title.position = "plot",
             plot.caption = element_text(color = "grey40",
                                         size = 9,
                                         margin = margin(20, 0, -20, 0)),
             plot.caption.position = "plot",
             axis.line.x = element_line(color = "black",
                                        size = .8),
             axis.line.y = element_line(color = "black",
                                        size = .8),
             axis.title.x = element_text(size = 16,
                                         face = "bold",
                                         margin = margin(t = 20)),
             axis.title.y = element_text(size = 16,
                                         face = "bold",
                                         margin = margin(r = 20)),
             axis.text = element_text(size = 11,
                                      color = "black",
                                      face = "bold"),
             axis.text.x = element_text(margin = margin(t = 10)),
             axis.text.y = element_text(margin = margin(r = 10)),
             axis.ticks = element_blank(),
             panel.grid.major.x = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.major.y = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.minor.x = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.minor.y = element_blank(),
             panel.spacing.x = unit(4, "lines"),
             panel.spacing.y = unit(2, "lines"),
             legend.position = "top",
             legend.title = element_text(family = "Montserrat",
                                         color = "black",
                                         size = 14,
                                         margin = margin(5, 0, 5, 0)),
             legend.text = element_text(family = "Montserrat",
                                        color = "black",
                                        size = 11,
                                        margin = margin(4.5, 4.5, 4.5, 4.5)),
             legend.background = element_rect(fill = NA,
                                              color = NA),
             legend.key = element_rect(color = NA, fill = NA),
             #legend.key.width = unit(5, "lines"),
             #legend.spacing.x = unit(.05, "pt"),
             #legend.spacing.y = unit(.55, "pt"),
             #legend.margin = margin(0, 0, 10, 0),
             strip.text = element_text(face = "bold",
                                       margin = margin(b = 10)))
## theme settings for flipped plots
theme_flip <-
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_line(size = .6,
                                          color = "#eaeaea"))
## theme settings for charts without y axis
theme_blank <- 
  theme(panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.line.y = element_blank(),
        axis.text.y = element_blank())

## numeric format for labels
num_format <- scales::format_format(big.mark = ",", small.mark = ",", scientific = F)
## main color backlinko
bl_col <- "#00d188"
bl_dark <- darken(bl_col, .3, space = "HLS")
```


# Keyword length

```{r}
write_length_volume <- function()
{
  get_length_volume <-  function(l)
  {
    sql <- glue(
          "SELECT SUM(COALESCE(keyword_info_search_volume / 10000, 0)) as `volume`, count(keyword_info_search_volume) as `count`
           FROM `dataforseo-bigquery.dataforseo_data.keyword_data`
           WHERE location = 2840
           AND keyword_info_search_volume IS NOT NULL
           AND spell = ''
           AND keyword_info_search_volume > 0
           AND LENGTH(keyword) = {l}")
        tb <- bq_project_query("dataforseo-bigquery", sql)
        bq_table_download(tb) %>% mutate(length = l, volume = volume * 10000)
  }
  
  df <- map_df(1:100, get_length_volume)  
  write_csv(df, "../proc_data/keyword_length_volume.csv")
}
#write_length_volume()
```

```{r}
write_length_volume <- function()
{
  get_length_volume <-  function(l)
  {
    sql <- glue(
          "SELECT SUM(COALESCE(keyword_info_search_volume / 10000, 0)) as `volume`, count(keyword_info_search_volume) as `count`
           FROM `dataforseo-bigquery.dataforseo_data.keyword_data`
           WHERE location = 2840
           AND keyword_info_search_volume IS NOT NULL
           AND keyword_info_search_volume > 0
           AND spell = ''
           AND (LENGTH(keyword) - LENGTH(replace(keyword, ' ', ''))) = {l}")
        tb <- bq_project_query("dataforseo-bigquery", sql)
        bq_table_download(tb) %>% mutate(length = l, volume = volume * 10000)
  }
  
  df <- map_df(1:40, get_length_volume)  
  write_csv(df, "../proc_data/keyword_word_volume.csv")
}
#write_length_volume()
```



```{r keyword_length_volume, fig.width = 10, fig.height = 6}
kw_length <- read_csv("../proc_data/keyword_length_volume.csv") %>% 
    drop_na()

kw_length %>% filter(length <= 50) %>% 
    mutate(prop = volume / sum(volume)) %>% 
    ggplot(aes(x = length, y = prop)) +
    geom_line(color = colorspace::desaturate(bl_col, .35), size = 1) + 
    geom_point(color = bl_dark, size = 2.5) +
    scale_x_continuous(expand = c(.008, .008)) +
    scale_y_continuous(labels = scales::label_percent(accuracy = 1), breaks = seq(0, .14, by = .02)) +
    labs(x = "Search term length (in characters)", y = "Total search volume", title = "Keywords Between 5-10 Characters Get Searched For the Most") +
    theme(panel.grid.minor.x = element_blank()) +
  ggsave(here::here("plots", "reworked", "volume_keywordlength.pdf"),
         width = 10, height = 6, device = cairo_pdf)
```

```{r, render = pander}
tbl <- tibble(
    mean = round(weighted.mean(kw_length$length, kw_length$volume), 1),
    median = round(spatstat::weighted.median(kw_length$length, kw_length$volume), 1)
) 
tbl %>% write_csv("../plots/csv/keyword_length.csv")
tbl
```

```{r keyword_length_count, fig.width = 10, fig.height = 6, eval = F}
kw_length %>% filter(length <= 50) %>% 
    mutate(prop = count / sum(count)) %>% 
    ggplot(aes(x = length, y = prop)) +
    geom_line(color = colorspace::desaturate(bl_col, .35), size = 1) + 
    geom_point(color = bl_dark, size = 2.5) +
    scale_x_continuous(expand = c(.008, .008)) +
    scale_y_continuous(labels = scales::label_percent(accuracy = 1), breaks = seq(0, .14, by = .02)) +
    labs(x = "Search term length (in characters)", y = "Total search volume", title = "Keywords Between 5-10 Characters Get Searched For the Most") +
    theme(panel.grid.minor.x = element_blank()) +
  ggsave(here::here("plots", "reworked", "volume_keywordlength_count.pdf"),
         width = 10, height = 6, device = cairo_pdf)
```



```{r keyword_words_volume, fig.width = 10, fig.height = 6}
kw_words <- vroom("../proc_data/keyword_word_volume.csv") %>% 
    drop_na()

kw_words %>% 
    mutate(prop = volume / sum(volume)) %>% 
    filter(length <= 8) %>% 
    ggplot(aes(x = length, y = prop)) +
    geom_line(color = colorspace::desaturate(bl_col, .35), size = 1) + 
    geom_point(color = bl_dark, size = 2.5) +
    scale_x_continuous(expand = c(.012, .012), breaks = seq(0, 10, by = 1)) +
    scale_y_continuous(labels = scales::label_percent(accuracy = 1), breaks = seq(0, .6, by = .1)) +
    labs(x = "Search term length (in words)", y = "Proportion of total search volume", title = "1–2 Word Terms Have The Highest Average Search Volume") +
    theme(panel.grid.minor.x = element_blank()) +
  ggsave(here::here("plots", "reworked", "volume_words_searchterm.pdf"),
         width = 10, height = 6, device = cairo_pdf)
```

```{r, render = pander}
tbl <- tibble(
    mean = round(weighted.mean(kw_words$length, kw_words$volume), 1),
    median = round(spatstat::weighted.median(kw_words$length,kw_words$volume), 1)
) 
tbl %>% write_csv("../plots/csv/keyword_count.csv")
tbl
```


Figure out how much more volume is from searches with 5+ words compared to 3 or less.

```{r}
kw_words %>% mutate(
    cat = case_when(
        length <= 3 ~ "<= 3",
        length >= 6 ~ ">= 5"
)) %>% 
    group_by(cat) %>% 
    summarise(vol = sum(volume),
              n = sum(count)) %>% 
    drop_na() %>% 
    mutate(ratio = vol / n)
```

```{r}
279.01025 / 27.23202
```



```{r keyword_words_count, fig.width = 10, fig.height = 6}
kw_words %>% 
    mutate(prop = count / sum(count)) %>% 
    filter(length <= 8) %>% 
    ggplot(aes(x = length, y = prop)) +
    geom_line(color = colorspace::desaturate(bl_col, .35), size = 1) + 
    geom_point(color = bl_dark, size = 2.5) +
    scale_x_continuous(expand = c(.008, .008), breaks = seq(0, 10, by = 1)) +
    scale_y_continuous(labels = scales::label_percent(accuracy = 1), breaks = seq(0, .6, by = .1)) +
    labs(x = "Search term length (in words)", y = "Proportion of total search volume", title = "Search volume by number of words in search term") +
    theme(panel.grid.minor.x = element_blank())
```

