---
title: "Keyword landscape analysis - ahrefs"
author: ""
date: "Last updated on `r Sys.Date()`"
output:
  html_document:
    theme: paper
    highlight: kate
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: true
editor_options: 
  chunk_output_type: inline
---


<style>
.list-group-item.active, .list-group-item.active:hover, .list-group-item.active:focus {
  background-color: #00d188;
  border-color: #00d188;
}

body {
  font-family: montserrat;
  color: #444444;
  font-size: 14px;
}

h1 {
  font-weight: bold;
  font-size: 28px;
}

h1.title {
  font-size: 30px;
  color: #00d188;
}

h2 {
  font-size: 24px;
}

h3 {
  font-size: 18px;
}
</style>



```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = F, message = F, fig.path = "../plots/1611/", cache = F, fig.showtext = TRUE, dpi = 700)

knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", small.mark = ",", scientific = F)
})

Sys.setlocale("LC_TIME", "C")
extrafont::loadfonts(device = "win")
```


```{r prep}
set.seed(1)
required_packages <- c("tidyverse", "magrittr", "DBI", "bigrquery", "arrow","glue", "vroom","janitor", "gt", "ggwordcloud", "readxl", "ggthemes", "hrbrthemes", "extrafont", "plotly", "scales", "stringr", "gganimate", "here", "tidytext", "sentimentr", "scales", "DT", "here", "sm", "mblm", "glue", "fs", "knitr", "rmdformats", "janitor", "urltools", "colorspace", "pdftools", "showtext", "pander", "wordcloud2", "stopwords", "magicfor", "gapminder", "ggridges")
for(i in required_packages) { 
  if(!require(i, character.only = T)) {
    #  if package is not existing, install then load the package
    install.packages(i, dependencies = T)
  require(i, character.only = T)
  }
}
panderOptions('table.alignment.default', "left")
## quality of png's
dpi <- 750
## theme updates; please adjust to client´s website
#theme_set(ggthemes::theme_clean(base_size = 15))
theme_set(ggthemes::theme_clean(base_size = 15, base_family = "Montserrat"))
theme_update(plot.margin = margin(30, 30, 30, 30),
             plot.background = element_rect(color = "white",
                                            fill = "white"),
             plot.title = element_text(size = 20,
                                       face = "bold",
                                       lineheight = 1.05,
                                       hjust = .5,
                                       margin = margin(10, 0, 25, 0)),
             plot.title.position = "plot",
             plot.caption = element_text(color = "grey40",
                                         size = 9,
                                         margin = margin(20, 0, -20, 0)),
             plot.caption.position = "plot",
             axis.line.x = element_line(color = "black",
                                        size = .8),
             axis.line.y = element_line(color = "black",
                                        size = .8),
             axis.title.x = element_text(size = 16,
                                         face = "bold",
                                         margin = margin(t = 20)),
             axis.title.y = element_text(size = 16,
                                         face = "bold",
                                         margin = margin(r = 20)),
             axis.text = element_text(size = 11,
                                      color = "black",
                                      face = "bold"),
             axis.text.x = element_text(margin = margin(t = 10)),
             axis.text.y = element_text(margin = margin(r = 10)),
             axis.ticks = element_blank(),
             panel.grid.major.x = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.major.y = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.minor.x = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.minor.y = element_blank(),
             panel.spacing.x = unit(4, "lines"),
             panel.spacing.y = unit(2, "lines"),
             legend.position = "top",
             legend.title = element_text(family = "Montserrat",
                                         color = "black",
                                         size = 14,
                                         margin = margin(5, 0, 5, 0)),
             legend.text = element_text(family = "Montserrat",
                                        color = "black",
                                        size = 11,
                                        margin = margin(4.5, 4.5, 4.5, 4.5)),
             legend.background = element_rect(fill = NA,
                                              color = NA),
             legend.key = element_rect(color = NA, fill = NA),
             #legend.key.width = unit(5, "lines"),
             #legend.spacing.x = unit(.05, "pt"),
             #legend.spacing.y = unit(.55, "pt"),
             #legend.margin = margin(0, 0, 10, 0),
             strip.text = element_text(face = "bold",
                                       margin = margin(b = 10)))
## theme settings for flipped plots
theme_flip <-
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_line(size = .6,
                                          color = "#eaeaea"))
## theme settings for charts without y axis
theme_blank <- 
  theme(panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.line.y = element_blank(),
        axis.text.y = element_blank())

## numeric format for labels
num_format <- scales::format_format(big.mark = ",", small.mark = ",", scientific = F)
## main color backlinko
bl_col <- "#00d188"
bl_dark <- darken(bl_col, .3, space = "HLS")
```


# Read data

```{r}
df <- read_feather("../proc_data/ahref/ahref.f")
```




# Global volume

```{r}
dfv <- 
  bind_rows(
    df %>% mutate(region = "US"),
    df %>% mutate(volume = global_volume - volume, region = "International")
    )
```

In *ahref*, international volume is higher:

```{r}
dfv %>% group_by(region) %>% 
  summarise(volume = sum(volume, na.rm = T)) %>% 
  mutate(volume = scales::percent(volume / sum(volume))) %>% 
  pander()
```

However, in the original data set, US volume is much higher:


```{r}
tribble(~region, ~volume,
        "US", "82%",
        "International", "19%")
```

I will be going by *ahref* in the following.

Internationally there are more searches with very low volume, while US has more searches with medium volume.




```{r comparison_count, fig.width = 10, fig.height = 6}
dfv %>% drop_na(volume) %>% 
  mutate(volume_group = case_when(volume < 100 ~ "< 100",
    between(volume, 100, 1000) ~ "100 - 1000",
    between(volume, 1000, 10000) ~ "1000 - 10,000",
    volume > 10000 ~ "10,000 +")) %>% 
  mutate(volume_group = factor(volume_group, levels = c("< 100", "100 - 1000", "1000 - 10,000", "10,000 +"))) %>% 
  group_by(volume_group, region) %>% 
  summarise(n = n()) %>% 
  ungroup() %>% 
  mutate(n = n / sum(n)) %>% 
  ggplot(aes(x = volume_group, y = n, fill = region)) +
  geom_bar(stat = "identity", position = position_dodge(), width = 0.8, color = "black") +
  labs(fill = "Region", x = "Volume", y = NULL) +
  scale_y_continuous(labels = scales::percent, expand = c(0,0)) +
  scale_fill_manual(values = c("grey70", bl_col), name = NULL) +
  theme(panel.grid.major.x = element_blank(), legend.position = c(.7, .8),
        legend.text = element_text(size = 14, color = "grey40", face = "bold")) +
  ggsave(here::here("plots", "reworked_font", "volume_region.pdf"),
         width = 10, height = 6, device = cairo_pdf)
```
There is not a large difference in the number of searches with very high volume. However, the total volume of these searches is a lot higher internationally


```{r comparison_volume, fig.width = 10, fig.height = 6}
dfv %>% drop_na(volume) %>% 
  mutate(volume_group = case_when(volume < 100 ~ "< 100",
    between(volume, 100, 1000) ~ "100 - 1000",
    between(volume, 1000, 10000) ~ "1000 - 10,000",
    between(volume, 10000, 100000) ~ "10,000 - 100,000",
    between(volume, 100000, 1000000) ~ "100,000 - 1M",
    volume > 1000000 ~ "1M +")) %>% 
  mutate(volume_group = factor(volume_group, levels = c("< 100", "100 - 1000", "1000 - 10,000", "10,000 - 100,000", "100,000 - 1M", "1M +"))) %>% 
  group_by(volume_group, region) %>% 
  summarise(n = sum(volume)) %>%
  ungroup() %>% 
  mutate(n = n / sum(n)) %>% 
  ggplot(aes(x = volume_group, y = n, fill = region)) +
  geom_bar(stat = "identity", position = position_dodge(), width = 0.8, color = "black") +
  labs(fill = "Region", x = "Volume", y = NULL) +
  scale_y_continuous(labels = scales::percent, expand = c(0,0)) +
  scale_fill_manual(values = c("grey70", bl_col), name = NULL) +
  theme(panel.grid.major.x = element_blank(), legend.position = c(.2, .5),
        legend.text = element_text(size = 14, color = "grey40", face = "bold")) +
  ggsave(here::here("plots", "reworked_font", "volume_region_high.pdf"),
         width = 10, height = 6, device = cairo_pdf)
```


?? CEDRIC: Percentage correct here? Was decimal numbers before but no clue why.


```{r international_v_us_volume, fig.width = 10, fig.height = 8.5}
df_int <- df %>% mutate(international_volume = global_volume - volume) %>% 
  filter(international_volume > 0, global_volume > 0) %>% 
  mutate(volume_diff = log10(international_volume) - log10(volume))

df_int_s <- df_int %>% sample_n(200000)

df_int_s %>% 
  ggplot(aes(x = volume, y = international_volume)) +
  geom_jitter(size = 0.1, alpha = 0.05, height = 0.15, width = 0.15, color = colorspace::desaturate(bl_dark, .3)) +
  geom_abline(intercept = 0, slope = 1, color = bl_col, size = 1) +
  scale_x_log10(labels = comma, expand = c(0,0)) +
  scale_y_log10(labels = comma, expand = c(0,0)) +
  labs(x = "US volume", y = "International volume", title = "Popular Searches in the US Tend to Be Popular Internationally") +
  ggsave(here::here("plots", "reworked", "volume_region_corr.pdf"),
         width = 10, height = 6, device = cairo_pdf)

df_int_s %>% 
  ggplot(aes(x = volume, y = international_volume)) +
  geom_hex(color = "white") +
  geom_abline(intercept = 0, slope = 1, color = bl_col, size = 1) +
  scale_x_log10(labels = comma, expand = c(.03, .03)) +
  scale_y_log10(labels = comma, expand = c(.03, .03)) +
  scale_fill_gradient(low = "grey85", high = bl_dark, 
                      name = "Number of observations",
                      breaks = seq(500, 9500, by = 1500)) +
  guides(fill = guide_colorbar(title.position = "top", 
                               title.hjust = .5,
                               direction = "horizontal",
                               barwidth = unit(16, "lines"),
                               barheight = unit(.4, "lines"))) +
  labs(x = "US volume", y = "International volume") +
  theme(legend.title = element_text(size = 10),
        legend.text = element_text(size = 8),
        legend.position = c(.75, .1)) +
  ggsave(here::here("plots", "reworked_font", "volume_region_corr_hex.pdf"),
         width = 10, height = 8.5, device = cairo_pdf)
```

<br>

We can see that they mostly follow each other, but there are some searches with large difference between them.

Higher volume internationally:

```{r}
tbl <- df_int %>% 
  arrange(desc(volume_diff)) %>% 
  filter(volume != 60) %>% 
  select(keyword, us_volume = volume, international_volume) %>% 
  head(5)

tbl %>% write_csv("../plots/csv/table_int.csv")
tbl %>% pander()
```

<br>

Higher volume in US:

```{r}
tbl <- df_int %>% 
  arrange(volume_diff) %>% 
  select(keyword, us_volume = volume, international_volume) %>% 
  head(5)

tbl %>% write_csv("../plots/csv/table_us.csv")
tbl %>% pander()
```

<br>


Searches that have higher volume in US have a higher click-per-search on average than searches that have higher volume internationally.

```{r international_cps}
df_int_s %>% 
  filter(cps < 5) %>% 
  ggplot(aes(x = volume_diff, y = cps)) +
  geom_point(size = 0.3, alpha = 0.05, color = "grey20") +
  geom_smooth(method='lm', formula= y~x, color = bl_col, size = 2) +
  scale_x_continuous(breaks = c(-2, 0, 3), labels = c("More US", "0", "More international")) +
  labs(x = NULL, y = "Cost per sale (CPS)") +
  ggsave(here::here("plots", "reworked_font", "volume_region_cps_corr.pdf"),
         width = 10, height = 7, device = cairo_pdf)
```
<br>

They also have a higher cost-per-click on average

```{r international_cpc, fig.width = 10, fig.height = 7}
df_int_s %>% 
  ggplot(aes(x = volume_diff, y = cpc)) +
  geom_point(size = 0.3, alpha = 0.05, color = "grey20") +
  geom_smooth(method='lm', formula= y~x, color = bl_col, size = 2) +
  scale_x_continuous(breaks = c(-2, 0, 3), labels = c("More US", "0", "More international")) +
  scale_y_log10(labels = comma) +
  labs(x = NULL, y = "CPC") +
  ggsave(here::here("plots", "reworked_font", "volume_region_cpc_corr.pdf"),
         width = 10, height = 7, device = cairo_pdf)
```
<br>

Searches that have higher volume internationally, tend to have higher difficulty

```{r international_difficulty, fig.width = 10, fig.height = 7}
df_int_s %>% 
  ggplot(aes(x = volume_diff, y = difficulty)) +
  geom_point(size = 0.3, alpha = 0.05, color = "grey20") +
  geom_smooth(method='lm', formula= y~x, color = bl_col, size = 2) +
  scale_x_continuous(breaks = c(-2, 0, 3), labels = c("More US", "0", "More international")) +
  labs(x = NULL, y = "Difficulty") +
  ggsave(here::here("plots", "reworked_font", "volume_region_difficulty_corr.pdf"),
         width = 10, height = 7, device = cairo_pdf)
```

<br>

## Other countries


```{r}
loc <- jsonlite::read_json("../raw_data/locations_stats.json")
magic_for(print, silent = TRUE)
for (i in 1:67){
    country <- loc$tasks[[1]]$result[[i]]$location_name
    code <- loc$tasks[[1]]$result[[i]]$location_code
    
    print(country)
    print(code)
}
countries <- magic_result_as_dataframe() %>% 
    left_join(
        gapminder %>% 
            filter(year == 2007),
        by = "country")
```




```{r}
write_locations_cpc <- function(){
    magic_for(print, silent = TRUE)
    for (code in countries$code){
        sql <- glue("SELECT AVG(keyword_info_cpc) as cpc
                    FROM `dataforseo-bigquery.dataforseo_data.keyword_data`
                  WHERE location = {code} 
                  AND keyword_info_search_volume > 0
                  ")
        tb <- bq_project_query("dataforseo-bigquery", sql)
        df <- bq_table_download(tb) 
        cpc <-  df$cpc
        print(cpc)
        }
    locations_cpc <- magic_result_as_dataframe()
    write_csv(locations_cpc, "../raw_data/locations_cpc.csv")
}
#write_locations_cpc()
locations_cpc <- read_csv("../raw_data/locations_cpc.csv")
```


```{r}
write_locations_volume <- function(){
    magic_for(print, silent = TRUE)
    for (code in countries$code){
        sql <- glue("SELECT SUM(keyword_info_search_volume) / 10000 as volume
                    FROM `dataforseo-bigquery.dataforseo_data.keyword_data`
                  WHERE location = {code} 
                  AND keyword_info_search_volume > 0
                  ")
        tb <- bq_project_query("dataforseo-bigquery", sql)
        df <- bq_table_download(tb) 
        volume <-  df$volume * 10000
        print(volume)
        }
    locations_volume <- magic_result_as_dataframe()
    write_csv(locations_volume, "../raw_data/locations_volume.csv")
}
#write_locations_volume()
locations_volume <- read_csv("../raw_data/locations_volume.csv")
```

There is only data for 5 English speaking countries

```{r}
countries <- inner_join(
    locations_volume,
    locations_cpc,
    by = "code") %>% 
    left_join(countries, by = "code") %>% 
    drop_na(volume)
countries$country
```
```{r}
countries %>% mutate(volume_prop = countries %>% filter(country == "United States") %>% pull(volume) / volume)
```


```{r search_volume_vs_us}
countries %>% mutate(volume_prop = volume / countries %>% filter(country == "United States") %>% pull(volume)) %>% 
    filter(country != "United States") %>% 
     ggplot(aes(x = reorder(country, volume_prop), y = volume_prop)) +
    geom_bar(stat = "identity", fill = bl_dark, width = 0.85, color = "black") +
    scale_y_continuous(labels = scales::percent, expand = c(.003, .003)) +
    theme(panel.grid.major.x = element_blank()) +
    labs(y = "", x = NULL, title = "Total search volume as proportion of US volume") +
    geom_text(aes(label = glue::glue("{format(round(volume_prop, 3) * 100, scientific = FALSE)}%")), nudge_y = .008, family = "Montserrat", fontface = "bold", color = "grey40")
```

```{r, eval = F}
countries %<>% mutate(volume_per_pop = volume / pop)
    mutate(volume_per_pop = volume / pop)

countries %>% filter(country == "United States") %>% pull(volume_per_pop) / 
    countries %>% filter(country == "United Kingdom") %>% pull(volume_per_pop)

countries %>% filter(country == "United States") %>% pull(volume_per_pop) / 
    countries %>% filter(country == "Canada") %>% pull(volume_per_pop)

countries %>% filter(country == "United States") %>% pull(volume_per_pop) / 
    countries %>% filter(country == "Australia") %>% pull(volume_per_pop)
    

countries
```



```{r, countries_volume, eval = F}
countries %<>% 
    mutate(volume_per_pop = volume / pop)
    #mutate(country = case_when(
    #    country == "United Kingdom" ~ "UK",
    #    country == "United States" ~ "US",
    #    T ~ country
    #)) %>% 
countries %>%     mutate(volume_per_pop = volume_per_pop / countries %>% filter(country == "United States") %>% pull(volume_per_pop)) %>% 
    filter(country != "United States") %>% 
    ggplot(aes(x = reorder(country, volume_per_pop), y = volume_per_pop)) +
    geom_bar(stat = "identity", fill = bl_dark, width = 0.85, color = "black") +
    geom_text(aes(label = format(round(mean_cpc, 2), scientific = FALSE)),
              nudge_y = -.02, family = "Montserrat", hjust = 1,
              size = 2.5, color = "white", fontface = "bold") +
    scale_y_continuous(labels = scales::percent, expand = c(.01, .01)) +
    theme(panel.grid.major.x = element_blank()) +
    labs(y = "Search volume per person", x = NULL, title = "Search volume per person compared to US") +
    geom_text(aes(label = glue::glue("{format(round(volume_per_pop, 3) * 100, scientific = FALSE)}%")), nudge_y = .04, family = "Montserrat", fontface = "bold", color = "grey40")
```



```{r, countries_cpc}
countries %>% 
    mutate(country = case_when(
        country == "United Kingdom" ~ "UK",
        country == "United States" ~ "US",
        T ~ country
    )) %>% 
    ggplot(aes(x = reorder(country, cpc), y = cpc)) +
    geom_bar(stat = "identity", fill = bl_dark, width = 0.85, color = "black") +
    geom_text(aes(label = format(round(cpc, 2), scientific = FALSE)),
            nudge_y = .025, family = "Montserrat", 
            fontface = "bold", color = "grey40") +
    scale_y_continuous( expand = c(.001, .001), limits = c(0, .64),
                        breaks = 0:6 / 10) +
    theme(panel.grid.minor.x = element_blank(), 
          panel.grid.major.x = element_blank()) +
    labs(y = "Mean CPC", x = NULL, title = "The US Has Higher CPCs Compared to Other English-Speaking Countries") +
  ggsave(here::here("plots", "reworked_font", "cpc_countries.pdf"),
         width = 10, height = 6, device = cairo_pdf)
```



```{r, countries_volume}
countries %>% 
    mutate(volume_per_pop = volume / pop) %>% 
    mutate(country = case_when(
        country == "United Kingdom" ~ "UK",
        country == "United States" ~ "US",
        T ~ country
    )) %>% 
    ggplot(aes(x = reorder(country, volume_per_pop), y = volume_per_pop)) +
    geom_bar(stat = "identity", fill = bl_dark, width = 0.85, color = "black") +
    geom_text(aes(label = format(round(volume_per_pop, 1), scientific = FALSE)),
            nudge_y = 30, family = "Montserrat", fontface = "bold", color = "grey40") +
  scale_y_continuous( expand = c(.001, .01), limits = c(0, 1100)) +
    theme(panel.grid.major.x = element_blank()) +
    labs(y = "Search volume per person", x = NULL, title = "Americans Search in Google More Than\nAny Other English-Speaking Countries") +
  ggsave(here::here("plots", "reworked_font", "volume_population.pdf"),
         width = 10, height = 6, device = cairo_pdf)
```


```{r international_v_us_volume, fig.width = 10, fig.height = 8.5}
df_int <- df %>% mutate(international_volume = global_volume - volume) %>% 
  filter(international_volume > 0, global_volume > 0) %>% 
  mutate(volume_diff = log10(international_volume) - log10(volume))

df_int_s <- df_int %>% sample_n(200000)

df_int_s %>% 
  ggplot(aes(x = volume, y = international_volume)) +
  geom_jitter(size = 0.1, alpha = 0.05, height = 0.15, width = 0.15, color = colorspace::desaturate(bl_dark, .3)) +
  geom_abline(intercept = 0, slope = 1, color = bl_col, size = 1) +
  scale_x_log10(labels = comma, expand = c(0,0)) +
  scale_y_log10(labels = comma, expand = c(0,0)) +
  labs(x = "US volume", y = "International volume") +
  ggsave(here::here("plots", "reworked_font", "volume_region_corr.pdf"),
         width = 10, height = 6, device = cairo_pdf)

df_int_s %>% 
  ggplot(aes(x = volume, y = international_volume)) +
  geom_hex(color = "white") +
  geom_abline(intercept = 0, slope = 1, color = bl_col, size = 1) +
  scale_x_log10(labels = comma, expand = c(.03, .03)) +
  scale_y_log10(labels = comma, expand = c(.03, .03)) +
  scale_fill_gradient(low = "grey85", high = bl_dark, 
                      name = "Number of observations",
                      breaks = seq(500, 9500, by = 1500)) +
  guides(fill = guide_colorbar(title.position = "top", 
                               title.hjust = .5,
                               direction = "horizontal",
                               barwidth = unit(16, "lines"),
                               barheight = unit(.4, "lines"))) +
  labs(x = "US volume", y = "International volume") +
  theme(legend.title = element_text(size = 10),
        legend.text = element_text(size = 8),
        legend.position = c(.75, .1)) +
  ggsave(here::here("plots", "reworked_font", "volume_region_corr_hex.pdf"),
         width = 10, height = 8.5, device = cairo_pdf)
```