---
title: "Spell type"
author: ""
date: "Last updated on `r Sys.Date()`"
output:
  html_document:
    theme: paper
    highlight: kate
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: true
editor_options: 
  chunk_output_type: inline
---


<style>
.list-group-item.active, .list-group-item.active:hover, .list-group-item.active:focus {
  background-color: #00d188;
  border-color: #00d188;
}

body {
  font-family: montserrat;
  color: #444444;
  font-size: 14px;
}

h1 {
  font-weight: bold;
  font-size: 28px;
}

h1.title {
  font-size: 30px;
  color: #00d188;
}

h2 {
  font-size: 24px;
}

h3 {
  font-size: 18px;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = F, message = F, fig.path = "../plots/", cache = F, fig.showtext = TRUE, dpi = 700)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", small.mark = ",", scientific = F)
})
Sys.setlocale("LC_TIME", "C")
extrafont::loadfonts(device = "win")
```



```{r prep}
set.seed(1)
required_packages <- c("tidyverse", "magrittr", "DBI", "bigrquery", "arrow","glue", "vroom","janitor", "gt", "ggwordcloud", "readxl", "ggthemes", "hrbrthemes", "extrafont", "plotly", "scales", "stringr", "gganimate", "here", "tidytext", "sentimentr", "scales", "DT", "here", "sm", "mblm", "glue", "fs", "knitr", "rmdformats", "janitor", "urltools", "colorspace", "pdftools", "showtext", "pander", "wordcloud2", "stopwords", "magicfor", "gapminder")
for(i in required_packages) { 
  if(!require(i, character.only = T)) {
    #  if package is not existing, install then load the package
    install.packages(i, dependencies = T)
  require(i, character.only = T)
  }
}
panderOptions('table.alignment.default', "left")
## quality of png's
dpi <- 750
## theme updates; please adjust to client´s website
#theme_set(ggthemes::theme_clean(base_size = 15))
theme_set(ggthemes::theme_clean(base_size = 15, base_family = "Montserrat"))
theme_update(plot.margin = margin(30, 30, 30, 30),
             plot.background = element_rect(color = "white",
                                            fill = "white"),
             plot.title = element_text(size = 20,
                                       face = "bold",
                                       lineheight = 1.05,
                                       hjust = .5,
                                       margin = margin(10, 0, 25, 0)),
             plot.title.position = "plot",
             plot.caption = element_text(color = "grey40",
                                         size = 9,
                                         margin = margin(20, 0, -20, 0)),
             plot.caption.position = "plot",
             axis.line.x = element_line(color = "black",
                                        size = .8),
             axis.line.y = element_line(color = "black",
                                        size = .8),
             axis.title.x = element_text(size = 16,
                                         face = "bold",
                                         margin = margin(t = 20)),
             axis.title.y = element_text(size = 16,
                                         face = "bold",
                                         margin = margin(r = 20)),
             axis.text = element_text(size = 11,
                                      color = "black",
                                      face = "bold"),
             axis.text.x = element_text(margin = margin(t = 10)),
             axis.text.y = element_text(margin = margin(r = 10)),
             axis.ticks = element_blank(),
             panel.grid.major.x = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.major.y = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.minor.x = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.minor.y = element_blank(),
             panel.spacing.x = unit(4, "lines"),
             panel.spacing.y = unit(2, "lines"),
             legend.position = "top",
             legend.title = element_text(family = "Montserrat",
                                         color = "black",
                                         size = 14,
                                         margin = margin(5, 0, 5, 0)),
             legend.text = element_text(family = "Montserrat",
                                        color = "black",
                                        size = 11,
                                        margin = margin(4.5, 4.5, 4.5, 4.5)),
             legend.background = element_rect(fill = NA,
                                              color = NA),
             legend.key = element_rect(color = NA, fill = NA),
             #legend.key.width = unit(5, "lines"),
             #legend.spacing.x = unit(.05, "pt"),
             #legend.spacing.y = unit(.55, "pt"),
             #legend.margin = margin(0, 0, 10, 0),
             strip.text = element_text(face = "bold",
                                       margin = margin(b = 10)))
## theme settings for flipped plots
theme_flip <-
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_line(size = .6,
                                          color = "#eaeaea"))
## theme settings for charts without y axis
theme_blank <- 
  theme(panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.line.y = element_blank(),
        axis.text.y = element_blank())

## numeric format for labels
num_format <- scales::format_format(big.mark = ",", small.mark = ",", scientific = F)
## main color backlinko
bl_col <- "#00d188"
bl_dark <- darken(bl_col, .3, space = "HLS")
```




```{r, cache}
con <- dbConnect(
    bigrquery::bigquery(),
    project = "dataforseo-bigquery",
    billing = "dataforseo-bigquery"
)
```


# Spell types


```{sql, connection = con, output.var = "sql"}
SELECT spell_type, SUM(keyword_info_search_volume) / 10000 AS `volume`
FROM `dataforseo-bigquery.dataforseo_data.keyword_data`
WHERE location = 2840
GROUP BY spell_type
```

```{r spell_types_volume, fig.width = 9}
spell_types <- sql %>% 
  mutate(spell_type = case_when(
    spell_type == "" ~ "No spell type",
    spell_type == "showing_results_for" ~ "Showing results for",
    spell_type == "did_you_mean" ~ "Did you mean",
    spell_type == "no_results_found_for" ~ "No results found for")) %>% 
  mutate(volume = volume / sum(volume))

spell_types %>% ggplot(aes(x = reorder(spell_type, volume), y = volume)) +
  geom_bar(stat = "identity", width = 0.8, fill = "turquoise4", color = "black") +
  labs(x = "", y = "", title = "Spell types - by volume") +
  scale_y_continuous(labels = scales::percent)
```


<br>

About half of search volume has a spell type. This is especially driven by misspellings of common domains. 

If going by count instead of by volume, almost none of the searches have a spell type:

```{sql, connection = con, output.var = "sql"}
SELECT spell_type, COUNT(spell_type) as n
FROM `dataforseo-bigquery.dataforseo_data.keyword_data`
WHERE location = 2840
ANd keyword_info_search_volume > 0
GROUP BY spell_type
```

```{r}
prop <- 1 - sql %>% filter(spell_type == "") %>% pull(n) / total_count
tibble("Proportion with spell type" = scales::percent(prop, accuracy = 0.001)) %>% pander()
```



```{r spell_types_count}
spell_types <- sql %>% 
  filter(spell_type != "") %>% 
  mutate(spell_type = case_when(
    spell_type == "" ~ "No spell type",
    spell_type == "showing_results_for" ~ "Showing results for",
    spell_type == "did_you_mean" ~ "Did you mean",
    spell_type == "no_results_found_for" ~ "No results found for"))

spell_types %>% mutate(prop = n / sum(n)) %>% 
  ggplot(aes(x = reorder(spell_type, prop), y = prop)) +
  geom_bar(stat = "identity", width = 0.8, fill = "turquoise4", color = "black") +
  labs(x = "", y = "", title = "Spell types - by count") +
  scale_y_continuous(labels = scales::percent)
```


!!!D: without spell type is missing "No spell type"

!!!J: This is on purpose, since only 1.38% has a spell type, as shown just above.

<br>


```{r}
tbl <- top %>% group_by(spell) %>% 
  summarise(volume = sum(keyword_info_search_volume)) %>% 
  arrange(desc(volume)) %>% 
  filter(spell != "") %>% 
  mutate(volume = scales::percent(volume / sum(volume), accuracy = 0.1)) %>% 
  head(10)# 

tbl %>% write_csv("../plots/csv/misspell.csv")

tbl %>% 
  gt() %>% 
  tab_options(table.align = "left") %>% 
  tab_header("Top 10 intended searches that are misspelled")
```
