---
title: "Keyword_info categories"
author: ""
date: "Last updated on `r Sys.Date()`"
output:
  html_document:
    theme: paper
    highlight: kate
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: true
editor_options: 
  chunk_output_type: inline
---


<style>
.list-group-item.active, .list-group-item.active:hover, .list-group-item.active:focus {
  background-color: #00d188;
  border-color: #00d188;
}

body {
  font-family: montserrat;
  color: #444444;
  font-size: 14px;
}

h1 {
  font-weight: bold;
  font-size: 28px;
}

h1.title {
  font-size: 30px;
  color: #00d188;
}

h2 {
  font-size: 24px;
}

h3 {
  font-size: 18px;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = F, message = F, fig.path = "../plots/1611/", cache = F, fig.showtext = TRUE, dpi = 700)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", small.mark = ",", scientific = F)
})
Sys.setlocale("LC_TIME", "C")
extrafont::loadfonts(device = "win")
```



```{r prep}
set.seed(1)
required_packages <- c("tidyverse", "magrittr", "DBI", "bigrquery", "arrow","glue", "vroom","janitor", "gt", "ggwordcloud", "readxl", "ggthemes", "hrbrthemes", "extrafont", "plotly", "scales", "stringr", "gganimate", "here", "tidytext", "sentimentr", "scales", "DT", "here", "sm", "mblm", "glue", "fs", "knitr", "rmdformats", "janitor", "urltools", "colorspace", "pdftools", "showtext", "pander", "wordcloud2", "stopwords", "magicfor", "gapminder")
for(i in required_packages) { 
  if(!require(i, character.only = T)) {
    #  if package is not existing, install then load the package
    install.packages(i, dependencies = T)
  require(i, character.only = T)
  }
}
panderOptions('table.alignment.default', "left")
## quality of png's
dpi <- 750
## theme updates; please adjust to client´s website
#theme_set(ggthemes::theme_clean(base_size = 15))
theme_set(ggthemes::theme_clean(base_size = 15, base_family = "Montserrat"))
theme_update(plot.margin = margin(30, 30, 30, 30),
             plot.background = element_rect(color = "white",
                                            fill = "white"),
             plot.title = element_text(size = 20,
                                       face = "bold",
                                       lineheight = 1.05,
                                       hjust = .5,
                                       margin = margin(10, 0, 25, 0)),
             plot.title.position = "plot",
             plot.caption = element_text(color = "grey40",
                                         size = 9,
                                         margin = margin(20, 0, -20, 0)),
             plot.caption.position = "plot",
             axis.line.x = element_line(color = "black",
                                        size = .8),
             axis.line.y = element_line(color = "black",
                                        size = .8),
             axis.title.x = element_text(size = 16,
                                         face = "bold",
                                         margin = margin(t = 20)),
             axis.title.y = element_text(size = 16,
                                         face = "bold",
                                         margin = margin(r = 20)),
             axis.text = element_text(size = 11,
                                      color = "black",
                                      face = "bold"),
             axis.text.x = element_text(margin = margin(t = 10)),
             axis.text.y = element_text(margin = margin(r = 10)),
             axis.ticks = element_blank(),
             panel.grid.major.x = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.major.y = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.minor.x = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.minor.y = element_blank(),
             panel.spacing.x = unit(4, "lines"),
             panel.spacing.y = unit(2, "lines"),
             legend.position = "top",
             legend.title = element_text(family = "Montserrat",
                                         color = "black",
                                         size = 14,
                                         margin = margin(5, 0, 5, 0)),
             legend.text = element_text(family = "Montserrat",
                                        color = "black",
                                        size = 11,
                                        margin = margin(4.5, 4.5, 4.5, 4.5)),
             legend.background = element_rect(fill = NA,
                                              color = NA),
             legend.key = element_rect(color = NA, fill = NA),
             #legend.key.width = unit(5, "lines"),
             #legend.spacing.x = unit(.05, "pt"),
             #legend.spacing.y = unit(.55, "pt"),
             #legend.margin = margin(0, 0, 10, 0),
             strip.text = element_text(face = "bold",
                                       margin = margin(b = 10)))
## theme settings for flipped plots
theme_flip <-
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_line(size = .6,
                                          color = "#eaeaea"))
## theme settings for charts without y axis
theme_blank <- 
  theme(panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.line.y = element_blank(),
        axis.text.y = element_blank())

## numeric format for labels
num_format <- scales::format_format(big.mark = ",", small.mark = ",", scientific = F)
## main color backlinko
bl_col <- "#00d188"
bl_dark <- darken(bl_col, .3, space = "HLS")
```




```{r}
overview <- read_csv("../proc_data/overview.csv")

con <- dbConnect(
    bigrquery::bigquery(),
    project = "dataforseo-bigquery",
    billing = "dataforseo-bigquery"
)
```





# Keyword_info categories

```{r}
pservices <- read_csv("../raw_data/productsservices.csv") %>% 
  clean_names() %>% rename(c1 = criterion_id) %>% select(-category) %>% 
  separate(c1, sep =",\"", into = c("id", "category")) %>% 
  mutate(category = substr(category, 2, nchar(category) -1)) %>% 
  separate(category, sep = "/", into = c("cat1", "cat2", "cat3", "cat4", "cat5", "cat6", "cat7", "cat8"))
toplevel <- pservices %>% filter(is.na(cat2))
```



```{r}
write_categories <- function()
{
  get_category_volume <-  function(id){
    sql <- glue(
      "SELECT Avg(keyword_info_search_volume) AS `search_volume`, COUNT(*) AS `count`
       FROM `dataforseo-bigquery.dataforseo_data.keyword_data`
       WHERE location = 2840 
       AND spell = ''
       AND keyword_info_categories like '%{id}%' ")
    tb <- bq_project_query("dataforseo-bigquery", sql)
    bq_table_download(tb) %>% mutate(id = id)
  }
  df <- map_df(toplevel$id, get_category_volume)  
  
  df %>% mutate(search_volume = search_volume,
                mean_volume = search_volume / count
                ) %>% 
    left_join(toplevel %>% select(id, cat1), by = "id") %>% 
    write_csv("../proc_data/categories_averages.csv")
}
#write_categories()
df <- read_csv("../proc_data/categories_averages.csv")
```


```{r search_category_volume_mean, fig.height = 10, fig.width = 7.5}
df %>% 
  ggplot(aes(x = fct_reorder(cat1, search_volume), y = search_volume)) +
  geom_bar(stat = "identity", fill = bl_dark, width = 0.7) +
  coord_flip() + 
  theme_flip +
  theme(panel.grid.major.y = element_blank(), axis.line.y = element_blank()) +
  scale_y_continuous(limits = c(0, 3500), expand = c(0,0), breaks = seq(0, 3000, by = 1000)) +
  labs(x = NULL, y = NULL, title = "Search volume mean by category")
```

!!!D: I would be curious to see the same graph with median. Wouldn´t it be better to use median given the skewed data set? 

!!!J: I am skeptical for using the median, since it is brought far down by a large number of searches with low volume, even when we exclude 0 volume searches. Remember, the median cpc overall was 0. But you are right that it is an issue with the skewed data set.

!!!D: Maybe a boxplot or something similiar would make more sense here? Or something like that: https://tinyurl.com/yxfwo5vt Leave that out if it´s too complicated to implement.  


```{r}
write_categories_volume <- function()
{
  get_category_volume <-  function(id){
    sql <- glue(
      "SELECT SUM(COALESCE(keyword_info_search_volume / 10000, 0)) as volume
       FROM `dataforseo-bigquery.dataforseo_data.keyword_data`
       WHERE location = 2840 
       AND spell = ''
       AND keyword_info_search_volume > 0
       AND keyword_info_categories like '%{id}%' ")
    tb <- bq_project_query("dataforseo-bigquery", sql)
    bq_table_download(tb) %>% mutate(id = id)
  }
  df <- map_df(toplevel$id, get_category_volume) %>% 
    mutate(volume = volume * 10000)
  
  df %>% left_join(toplevel %>% select(id, cat1), by = "id") %>% 
    write_csv("../proc_data/categories_total_volume.csv")
}
#write_categories_volume()
df <- read_csv("../proc_data/categories_total_volume.csv")
```

<br>

```{r search_category_total_volume, fig.height = 10, fig.width = 7.5}
df %>% 
  mutate(volume = volume / sum(volume)) %>% 
  ggplot(aes(x = fct_reorder(cat1, volume), y = volume)) +
  geom_bar(stat = "identity", fill = bl_dark, width = 0.7) +
  coord_flip() + 
  theme_flip +
  theme(panel.grid.major.y = element_blank(), axis.line.y = element_blank()) +
  scale_y_continuous(limits = c(0, .2), expand = c(0,0), labels = scales::percent) +
  labs(x = NULL, y = NULL, title = "Total search volume by category") +
  ggsave(here::here("plots", "reworked", "volume_total_category_ordered.pdf"),
         width = 10, height = 7.5, device = cairo_pdf)
```

<br>

```{r}
write_categories <- function()
{
  get_category <-  function(id){
    sql <- glue(
      "SELECT AVG(keyword_info_cpc) as mean_cpc
       FROM `dataforseo-bigquery.dataforseo_data.keyword_data`
       WHERE location = 2840 
       AND spell = ''
       AND keyword_info_search_volume > 0
       AND keyword_info_categories like '%{id}%' ")
    tb <- bq_project_query("dataforseo-bigquery", sql)
    bq_table_download(tb) %>% mutate(id = id)
  }
  df <- map_df(toplevel$id, get_category)  
  
  df %>% left_join(toplevel %>% select(id, cat1), by = "id") %>% 
    write_csv("../proc_data/categories_cpc.csv")
}
#write_categories()
df <- read_csv("../proc_data/categories_cpc.csv")
```

<br>

```{r search_category_cpc_mean, fig.height = 10, fig.width = 6.5}
df %>% 
  ggplot(aes(x = fct_reorder(cat1, mean_cpc), y = mean_cpc)) +
  geom_bar(stat = "identity", fill = bl_dark, width = 0.7) +
  coord_flip() + 
  theme_flip +
  theme(panel.grid.major.y = element_blank(), axis.line.y = element_blank()) +
  scale_y_continuous(limits = c(0, 2), expand = c(0,0)) +
  labs(x = NULL, y = NULL, title = "Mean CPC by category") +
  ggsave(here::here("plots", "reworked", "cpc_mean_category_ordered.pdf"),
         width = 10, height = 6.5, device = cairo_pdf)
```

<br>

