---
title: "Keyword landscape analysis"
author: ""
date: "Last updated on `r Sys.Date()`"
output:
  html_document:
    theme: paper
    highlight: kate
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: true
editor_options: 
  chunk_output_type: console
---


<style>
.list-group-item.active, .list-group-item.active:hover, .list-group-item.active:focus {
  background-color: #00d188;
  border-color: #00d188;
}

body {
  font-family: montserrat;
  color: #444444;
  font-size: 14px;
}

h1 {
  font-weight: bold;
  font-size: 28px;
}

h1.title {
  font-size: 30px;
  color: #00d188;
}

h2 {
  font-size: 24px;
}

h3 {
  font-size: 18px;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = F, message = F, fig.path = "../plots/", cache = F, fig.showtext = TRUE, dpi = 700)

knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", small.mark = ",", scientific = F)
})

Sys.setlocale("LC_TIME", "C")
extrafont::loadfonts(device = "win")
```



```{r prep}
set.seed(2)

required_packages <- c("tidyverse", "magrittr", "DBI", "bigrquery", "arrow","glue", "vroom","janitor", "gt", "ggwordcloud", "readxl", "ggthemes", "hrbrthemes", "extrafont", "plotly", "scales", "stringr", "gganimate", "here", "tidytext", "sentimentr", "scales", "DT", "here", "sm", "mblm", "glue", "fs", "knitr", "rmdformats", "janitor", "urltools", "colorspace", "pdftools", "showtext", "pander")
for(i in required_packages) { 
  if(!require(i, character.only = T)) {
    #  if package is not existing, install then load the package
    install.packages(i, dependencies = T)
  require(i, character.only = T)
  }
}

panderOptions('table.alignment.default', "left")

## quality of png's
dpi <- 750

## theme updates; please adjust to client´s website
#theme_set(ggthemes::theme_clean(base_size = 15))
theme_set(ggthemes::theme_clean(base_size = 15, base_family = "Montserrat"))


theme_update(plot.margin = margin(30, 30, 30, 30),
             plot.background = element_rect(color = "white",
                                            fill = "white"),
             plot.title = element_text(size = 20,
                                       face = "bold",
                                       lineheight = 1.05,
                                       hjust = .5,
                                       margin = margin(10, 0, 25, 0)),
             plot.title.position = "plot",
             plot.caption = element_text(color = "grey40",
                                         size = 9,
                                         margin = margin(20, 0, -20, 0)),
             plot.caption.position = "plot",
             axis.line.x = element_line(color = "black",
                                        size = .8),
             axis.line.y = element_line(color = "black",
                                        size = .8),
             axis.title.x = element_text(size = 16,
                                         face = "bold",
                                         margin = margin(t = 20)),
             axis.title.y = element_text(size = 16,
                                         face = "bold",
                                         margin = margin(r = 20)),
             axis.text = element_text(size = 11,
                                      color = "black",
                                      face = "bold"),
             axis.text.x = element_text(margin = margin(t = 10)),
             axis.text.y = element_text(margin = margin(r = 10)),
             axis.ticks = element_blank(),
             panel.grid.major.x = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.major.y = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.minor.x = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.minor.y = element_blank(),
             panel.spacing.x = unit(4, "lines"),
             panel.spacing.y = unit(2, "lines"),
             legend.position = "top",
             legend.title = element_text(family = "Montserrat",
                                         color = "black",
                                         size = 14,
                                         margin = margin(5, 0, 5, 0)),
             legend.text = element_text(family = "Montserrat",
                                        color = "black",
                                        size = 11,
                                        margin = margin(4.5, 4.5, 4.5, 4.5)),
             legend.background = element_rect(fill = NA,
                                              color = NA),
             legend.key = element_rect(color = NA, fill = NA),
             #legend.key.width = unit(5, "lines"),
             #legend.spacing.x = unit(.05, "pt"),
             #legend.spacing.y = unit(.55, "pt"),
             #legend.margin = margin(0, 0, 10, 0),
             strip.text = element_text(face = "bold",
                                       margin = margin(b = 10)))

## theme settings for flipped plots
theme_flip <-
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_line(size = .6,
                                          color = "#eaeaea"))

## theme settings for maps
theme_map <- 
  theme_void(base_family = "Montserrat") +
  theme(legend.direction = "horizontal",
        legend.box = "horizontal",
        legend.margin = margin(10, 10, 10, 10),
        legend.title = element_text(size = 17, 
                                    face = "bold"),
        legend.text = element_text(color = "grey33",
                                   size = 12),
        plot.margin = margin(15, 5, 15, 5),
        plot.title = element_text(face = "bold",
                                  size = 20,
                                  hjust = .5,
                                  margin = margin(30, 0, 10, 0)),
        plot.subtitle = element_text(face = "bold",
                                     color = "grey33",
                                     size = 17,
                                     hjust = .5,
                                     margin = margin(10, 0, -30, 0)),
        plot.caption = element_text(size = 14,
                                    color = "grey33",
                                    hjust = .97,
                                    margin = margin(-30, 0, 0, 0)))

## numeric format for labels
num_format <- scales::format_format(big.mark = ",", small.mark = ",", scientific = F)

## main color backlinko
bl_col <- "#00d188"
bl_dark <- darken(bl_col, .3, space = "HLS")

## colors + labels for interval stripes
int_cols <- c("#bce2d5", "#79d8b6", bl_col, "#009f66", "#006c45", "#003925")
int_perc <- c("100%", "95%", "75%", "50%", "25%", "5%")

## colors for degrees (Bachelors, Massters, Doctorate in reverse order)
cols_degree <- c("#e64500", "#FFCC00", darken(bl_col, .1))

## gradient colors for position
colfunc <- colorRampPalette(c(bl_col, "#bce2d5"))
pos_cols <- colfunc(10)
```


```{r common_functions}
display_number <- function(n, title){
  tibble(!!sym(title) := format(n, big.mark = ",")) %>% pander()
}
```


```{r, cache}
con <- dbConnect(
    bigrquery::bigquery(),
    project = "dataforseo-bigquery",
    billing = "dataforseo-bigquery"
)

sql <- glue("SELECT * FROM `dataforseo-bigquery.dataforseo_data.keyword_data` 
          WHERE location = 2840 
          ORDER BY keyword_info_search_volume DESC
          LIMIT 50000")
tb <- bq_project_query("dataforseo-bigquery", sql)
top <- bq_table_download(tb, max_results = 1000000)
```


# Basic stats

```{sql, connection = con, output.var = "sql"}
SELECT COUNT(keyword_info_search_volume) as `total_count`
FROM `dataforseo-bigquery.dataforseo_data.keyword_data`
WHERE `location` = 2840
```

```{r}
total_count <- sql$total_count
display_number(total_count, "Total number of different searches")
```

!!!D: Just curious: Can you explain what you mean with different number of searchers? I thought all the search queries were unique. 


```{sql, connection = con, output.var = "sql"}
SELECT SUM(COALESCE(keyword_info_search_volume / 10000, 0)) AS total_volume
FROM `dataforseo-bigquery.dataforseo_data.keyword_data`
WHERE location = 2840
```

```{r}
# Calculated in a roundabout way to avoid integer overflow
total_volume <- sql$total_volume * 10000
tibble("Total number of searches" = glue("~{format(round(total_volume / 1000000), big.mark = ',')} million")) %>% 
  pander()
```


<br>

This table shows the top 10 searches. They are almost all spelling errors. As in, they are not really searched, but rather people attempting to go to Youtube or Facebook, but typing it wrong. Oddly they are all attributed as having a search volume of exactly 185 million.

```{r}
top %>% 
  select(keyword, location, spell, spell_type, keyword_info_search_volume) %>% 
  head(10) %>% 
  gt() %>% 
  tab_options(table.align = "left") %>% 
  tab_header("Top searches")
```

```{sql, connection = con, output.var = "sql"}
SELECT COUNT(*) as `missing_count`
FROM `dataforseo-bigquery.dataforseo_data.keyword_data`
WHERE `location` = 2840
AND keyword_info_search_volume IS NULL
```

```{r}
missing_count <- sql$missing_count
tibble("Missing search volume" = scales::percent(missing_count / total_count, accuracy = 0.001)) %>% pander()
```

The missing have some searches that are likely high volume. Thus they are truly missing, and not just 0s.

```{sql, connection = con, output.var = "sql"}
SELECT keyword, keyword_info_search_volume
FROM `dataforseo-bigquery.dataforseo_data.keyword_data`
WHERE `location` = 2840
AND keyword_info_search_volume IS NULL
ORDER BY RAND()
LIMIT 10
```

```{r}
sql %>% gt() %>% tab_options(table.align = "left") %>% 
  tab_header("Keywords with missing search volume")
```


```{sql, connection = con, output.var = "sql"}
SELECT COUNT(*) as `zero_count`
FROM `dataforseo-bigquery.dataforseo_data.keyword_data`
WHERE `location` = 2840
AND keyword_info_search_volume = 0
```

```{r}
zero_count <- sql$zero_count
tibble("Searches with search volume 0" = scales::percent(zero_count / total_count, accuracy = 0.001)) %>% pander()
```

!!!D: 47.243% searches with 0 is quite high. Do you think it would make sense to remove those for the forthcoming analysis? 


```{r}
display_number(total_volume / total_count, "Mean search volume")
```


```{sql, connection = con, output.var = "sql"}
SELECT approx_quantiles(keyword_info_search_volume, 2)[offset(1)] AS `median`
FROM `dataforseo-bigquery.dataforseo_data.keyword_data`
WHERE location = 2840
```


```{r}
display_number(sql$median, "Median search volume")
```


```{sql, connection = con, output.var = "sql"}
SELECT AVG(`keyword_info_cpc`) AS `mean_cpc`
FROM `dataforseo-bigquery.dataforseo_data.keyword_data`
WHERE `location` = 2840
```


```{r}
display_number(sql$mean_cpc, "Mean CPC")
```


```{sql, connection = con, output.var = "sql"}
SELECT approx_quantiles(keyword_info_cpc, 2)[offset(1)] AS `median_cpc`
FROM `dataforseo-bigquery.dataforseo_data.keyword_data`
WHERE location = 2840
```


```{r}
display_number(sql$median_cpc, "Median CPC")
```

<br>

# Spell types


```{sql, connection = con, output.var = "sql"}
SELECT *
FROM `dataforseo-bigquery.dataforseo_data.keyword_data`
WHERE location = 2840
AND spell_type <> ""
AND keyword_info_search_volume < 10000
LIMIT 1000
```

```{sql, connection = con, output.var = "sql"}
SELECT spell_type, SUM(keyword_info_search_volume) / 10000 AS `volume`
FROM `dataforseo-bigquery.dataforseo_data.keyword_data`
WHERE location = 2840
GROUP BY spell_type
```

```{r spell_types}
spell_types <- sql %>% mutate(spell_type = ifelse(spell_type == "", "no_spell_type", spell_type)) %>% 
  mutate(volume = volume * 10000) 


spell_types %>% ggplot(aes(x = reorder(spell_type, volume), y = volume)) +
  geom_bar(stat = "identity", width = 0.8, fill = "turquoise4", color = "black") +
  labs(x = "", title = "Spell types")
```

!!!D: Can you provide a sentence on how you derived to that result? e.g. seems you only considered keywords with search volume above 10k. Why?

!!!D: x axis labels are not readable. Please replace the scientific notation for the y-axis. 

About half of search volume has a spell type. This is especially driven by misspellings of common domains. 

```{r}
spell_type_proportion <- spell_types %>% filter(spell_type != "no_spell_type") %$% 
  sum(volume) / total_volume
tibble("Proportion of searches with spell type" = scales::percent(spell_type_proportion, accuracy = 0.1)) %>% pander()
```

<br>



```{r}
top %>% group_by(spell) %>% 
  summarise(volume = sum(keyword_info_search_volume)) %>% 
  arrange(desc(volume)) %>% 
  filter(spell != "") %>% 
  head(15) %>% 
  gt() %>% 
  tab_options(table.align = "left") %>% 
  tab_header("Top 15 intended searches that are misspelled")
```

!!!D: not interested in total search volume. May be percentage share of all misspelled words?  

<br>

# Questions


```{r questions}
question_words <- c("what", "which", "where", "who", "why", "how")
questions <- tribble(~question, ~volume)
for (word in question_words){
  sql <- glue("SELECT sum(keyword_info_search_volume) FROM `dataforseo-bigquery.dataforseo_data.keyword_data`
            WHERE location = 2840 
            AND keyword like '{word} %' ")
  tb <- bq_project_query("dataforseo-bigquery", sql)
  df <- bq_table_download(tb) 
  questions %<>% add_row(question = word, volume = df$f0_)
}

questions %>% mutate(prop = volume / total_volume) %>% 
  ggplot(aes(x = reorder(question, prop), y = prop)) +
  geom_bar(stat = "identity", fill = "turquoise4", color = "black") +
  scale_y_continuous(labels = scales::percent, limits = c(0, 0.005), expand = c(0,0)) +
  labs(title = "Questions in searches", x = "", y = "")
```

!!!D: We are not interested in the total of sum of search volume (this applies to the whole data analysis excersise) but rather the counts (or percentage shares). 


```{sql, connection = con, output.var = "sql"}
SELECT SUM(COALESCE(keyword_info_search_volume / 10000, 0)) AS total_volume
FROM `dataforseo-bigquery.dataforseo_data.keyword_data`
WHERE location = 2840
AND spell_type = ""
```

```{r}
tibble("Total percentage of searches that are questions" = 
         scales::percent(questions %$% sum(volume) / total_volume, accuracy = 0.001)) %>% 
  pander()
```

<br>


```{r}
total_volume_nospell <- sql$total_volume * 10000

tibble("Total percentage of searches that are questions if spell types are removed" = 
         scales::percent(questions %$% sum(volume) / total_volume_nospell, accuracy = 0.001)) %>% 
  pander()
```

!!!D: Result for counts of words? 


<br>

# Stopwords


```{r stopwords, fig.height = 8, fig.width = 6}
stopwords_list <- tibble(stopword = stopwords::stopwords(language = "en")) %>% 
  mutate(stopword = str_remove(stopword, "'")) %>% 
  filter(!(stopword %in% c("shed", "wed", "ill", "hell", "shell")))

get_stopwords_counts <- function(){
stopwords <- tribble(~stopword, ~volume)
  for (word in stopword_list$stopword){
    print(word)
    sql <- glue(
      "SELECT SUM(COALESCE(keyword_info_search_volume / 1000, 0)) AS `total_volume` 
       FROM `dataforseo-bigquery.dataforseo_data.keyword_data`
       WHERE location = 2840 
       AND keyword like '% {word} %' OR keyword like '{word} %' OR keyword like '% {word}'")
    tb <- bq_project_query("dataforseo-bigquery", sql)
  
    df <- bq_table_download(tb) 
    stopwords %<>% add_row(stopword = word, volume = df$total_volume * 1000)
  }
  
  write_csv(stopwords, "../proc_data/stopwords.csv")
}
stopwords <- read_csv("../proc_data/stopwords.csv")

stopwords %>% mutate(prop = volume / total_volume) %>%
  filter(prop > 0.001) %>% 
  ggplot(aes(x = reorder(stopword, prop), y = prop)) +
  geom_bar(stat = "identity", color = "black", fill = "turquoise4", width = 0.7) +
  scale_y_continuous(labels = scales::percent, expand = c(0,0), limits = c(0, 0.05)) +
  labs(x = "", y = "", title = "Searches with specific stopwords") +
  coord_flip()
```

!!!D: the graph is not that insightful. Please make the wordcloud a bit more readable and visually appealing. Feel to add more than 25 words. 


<br>



```{r stopwords_wordcloud}
set.seed(2)
stopwords %>% 
  mutate(stopword = ifelse(stopword == "i", "I", stopword)) %>% 
  arrange(desc(volume)) %>% 
  head(25) %>% 
  ggplot(aes(label = stopword, size = volume, color = factor(sample.int(10, 25, replace = TRUE)))) +
  geom_text_wordcloud(perc_step = 0.5) +
  scale_size_area(max_size = 30) +
  theme_minimal()
```




<br>

# Search tails

```{r search_tails}
volume_top <- top %>%  
  add_rownames() %>% 
  mutate(rowname = as.numeric(rowname)) %>% 
  select(rowname, volume = keyword_info_search_volume)

ylab <- c(50, 100, 150, 200)

volume_top %>% 
  mutate(cat = case_when(
    rowname < 500 ~ "Top 500",
    rowname < 1000 ~ "Top 1000",
    rowname < 2000 ~ "Top 2000",
    rowname < 5801 ~ "Top 0.001%",
    T ~ "Remaining 99.99%"
  )) %>% 
  mutate(cat = factor(cat, levels = c("Top 500", "Top 1000", "Top 2000", "Top 0.001%", "Remaining 99.99%"))) %>% 
  head(10500) %>% 
  ggplot(aes(x = rowname, y = volume, fill = cat)) +
  geom_area(alpha = 0.8) +
  scale_y_continuous(
    labels = glue("{ylab} M"),
    breaks = 10^6 * ylab,
    limits = c(0, 200* 10^6), 
    expand = c(0,0)
    ) +
  labs(x = "", title = "Long tail") + 
  geom_segment(aes(x = 8000, y = 35*10^6, xend = 10500, yend = 35*10^6),
               arrow = arrow(length = unit(0.5, "cm"))) +
  scale_x_continuous(expand = c(0,0))
```



<br>

```{r search_tails2}
get_count_range <-  function(lower, higher)
{
  sql <- glue(
        "SELECT COUNT(*) AS `count` 
         FROM `dataforseo-bigquery.dataforseo_data.keyword_data`
         WHERE location = 2840 
         AND keyword_info_search_volume >= {lower} 
         AND keyword_info_search_volume <= {higher}")
      tb <- bq_project_query("dataforseo-bigquery", sql)
      bq_table_download(tb)$count
}

df <- tribble(
  ~cat, ~count,
  "0 - 10", get_count_range(0, 10),
  "11- 100", get_count_range(11, 100),
  "101 - 1000", get_count_range(101, 1000),
  "1001 - 10000", get_count_range(1001, 10000),
  "10001 - 100000", get_count_range(10001, "100000"),
  "100001+", get_count_range("100001", "100000000000")) 


df %>% 
  mutate(count = count / sum(count)) %>% 
  ggplot(aes(x = reorder(cat, desc(count)), y = count)) +
  geom_bar(stat = "identity", fill = "turquoise4", color = "black") +
  theme_light() +
  labs(x = "", y = "", title = "Long tail") +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1), expand = c(0,0))
           
```
<br>


```{r}
write_length_volume <- function()
{
  get_length_volume <-  function(l)
  {
    sql <- glue(
          "SELECT sum(keyword_info_search_volume) / 10000 as `volume`, count(keyword_info_search_volume) as `count`
           FROM `dataforseo-bigquery.dataforseo_data.keyword_data`
           WHERE location = 2840
           AND keyword_info_search_volume IS NOT NULL
           AND LENGTH(keyword) = {l}")
        tb <- bq_project_query("dataforseo-bigquery", sql)
        bq_table_download(tb) %>% mutate(length = l)
  }
  
  df <- map_df(1:50, get_length_volume)  
  write_csv(df, "../proc_data/keyword_length_volume.csv")
}
```


!!!D: x axis labeling missing. Categories on top not readable. What does the arrow imply? 

```{r keyword_length_volume}
df <- read_csv("../proc_data/keyword_length_volume.csv")

df %>% mutate(
  volume = 10000 * volume,
  ratio = volume / count
) %>% 
  ggplot(aes(x = length, y = ratio)) +
  geom_line(color = "turquoise4", size = 1) + geom_point(color = "turquoise4") +
  theme_light() +
  labs(x = "", y = "", title = "Average search volume by keyword length")
```

!!!D: please label axis properly. Can you explain that pattern? One sentence finding. 

<br>


# Keyword_info categories

```{r}
pservices <- read_csv("../raw_data/productsservices.csv") %>% 
  clean_names() %>% rename(c1 = criterion_id) %>% select(-category) %>% 
  separate(c1, sep =",\"", into = c("id", "category")) %>% 
  mutate(category = substr(category, 2, nchar(category) -1)) %>% 
  separate(category, sep = "/", into = c("cat1", "cat2", "cat3", "cat4", "cat5", "cat6", "cat7", "cat8"))

toplevel <- pservices %>% filter(is.na(cat2))
```



```{r}
write_categories <- function()
{
  get_category_volume <-  function(id){
    sql <- glue(
      "SELECT SUM(keyword_info_search_volume) / 10000 AS `search_volume`, AVG(keyword_info_cpc) AS `cpc`, COUNT(*) AS `count`
       FROM `dataforseo-bigquery.dataforseo_data.keyword_data`
       WHERE location = 2840 
       AND keyword_info_categories like '%{id}%' ")
    tb <- bq_project_query("dataforseo-bigquery", sql)
    bq_table_download(tb) %>% mutate(id = id)
  }

  df <- map_df(toplevel$id, get_category_volume)  
  
  df %>% mutate(search_volume = search_volume * 10000,
                mean_volume = search_volume / count
                ) %>% 
    left_join(toplevel %>% select(id, cat1), by = "id") %>% 
    write_csv("../proc_data/categories_averages.csv")
}

df <- read_csv("../proc_data/categories_averages.csv")
```


```{r search_category, fig.height = 6, fig.width = 7}
df %>% 
  ggplot(aes(x = fct_rev(cat1), y = mean_volume)) +
  geom_bar(stat = "identity", fill = "turquoise4", color = "black", width = 0.8) +
  theme_light() +
  coord_flip() +
  scale_y_continuous(limits = c(0, 9000), expand = c(0,0)) +
  labs(x = "", y = "", title = "Search volume mean by category")
```

!!!D: I would be curious to see the same graph with median. Wouldn´t it be better to use median given the skewed data set? 

<br>

```{r cpc_category, fig.height = 6, fig.width = 7}
df %>% 
  ggplot(aes(x = fct_rev(cat1), y = cpc)) +
  geom_bar(stat = "identity", fill = "turquoise4", color = "black", width = 0.8) +
  theme_light() +
  coord_flip() +
  scale_y_continuous(limits = c(0, 2), expand = c(0,0)) +
  labs(x = "", y = "", title = "CPC mean by category")
```

!!!D: I would be curious to see the same graph with median. Wouldn´t it be better to use median given the skewed data set? 