---
title: "Keyword landscape analysis - ahrefs"
author: ""
date: "Last updated on `r Sys.Date()`"
output:
  html_document:
    theme: paper
    highlight: kate
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: true
editor_options: 
  chunk_output_type: inline
---


<style>
.list-group-item.active, .list-group-item.active:hover, .list-group-item.active:focus {
  background-color: #00d188;
  border-color: #00d188;
}

body {
  font-family: montserrat;
  color: #444444;
  font-size: 14px;
}

h1 {
  font-weight: bold;
  font-size: 28px;
}

h1.title {
  font-size: 30px;
  color: #00d188;
}

h2 {
  font-size: 24px;
}

h3 {
  font-size: 18px;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = F, message = F, fig.path = "../plots/", cache = F, fig.showtext = TRUE, dpi = 700)

knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", small.mark = ",", scientific = F)
})

Sys.setlocale("LC_TIME", "C")
extrafont::loadfonts(device = "win")
```




```{r prep}
set.seed(2)

required_packages <- c("tidyverse", "magrittr", "DBI", "bigrquery", "arrow","glue", "vroom","janitor", "gt", "ggwordcloud", "readxl", "ggthemes", "hrbrthemes", "extrafont", "plotly", "scales", "stringr", "gganimate", "here", "tidytext", "sentimentr", "scales", "DT", "here", "sm", "mblm", "glue", "fs", "knitr", "rmdformats", "janitor", "urltools", "colorspace", "pdftools", "showtext", "pander", "ggridges")
for(i in required_packages) { 
  if(!require(i, character.only = T)) {
    #  if package is not existing, install then load the package
    install.packages(i, dependencies = T)
  require(i, character.only = T)
  }
}

panderOptions('table.alignment.default', "left")

## quality of png's
dpi <- 750

## theme updates; please adjust to client´s website
#theme_set(ggthemes::theme_clean(base_size = 15))
theme_set(ggthemes::theme_clean(base_size = 15, base_family = "Montserrat"))


theme_update(plot.margin = margin(30, 30, 30, 30),
             plot.background = element_rect(color = "white",
                                            fill = "white"),
             plot.title = element_text(size = 20,
                                       face = "bold",
                                       lineheight = 1.05,
                                       hjust = .5,
                                       margin = margin(10, 0, 25, 0)),
             plot.title.position = "plot",
             plot.caption = element_text(color = "grey40",
                                         size = 9,
                                         margin = margin(20, 0, -20, 0)),
             plot.caption.position = "plot",
             axis.line.x = element_line(color = "black",
                                        size = .8),
             axis.line.y = element_line(color = "black",
                                        size = .8),
             axis.title.x = element_text(size = 16,
                                         face = "bold",
                                         margin = margin(t = 20)),
             axis.title.y = element_text(size = 16,
                                         face = "bold",
                                         margin = margin(r = 20)),
             axis.text = element_text(size = 11,
                                      color = "black",
                                      face = "bold"),
             axis.text.x = element_text(margin = margin(t = 10)),
             axis.text.y = element_text(margin = margin(r = 10)),
             axis.ticks = element_blank(),
             panel.grid.major.x = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.major.y = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.minor.x = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.minor.y = element_blank(),
             panel.spacing.x = unit(4, "lines"),
             panel.spacing.y = unit(2, "lines"),
             legend.position = "top",
             legend.title = element_text(family = "Montserrat",
                                         color = "black",
                                         size = 14,
                                         margin = margin(5, 0, 5, 0)),
             legend.text = element_text(family = "Montserrat",
                                        color = "black",
                                        size = 11,
                                        margin = margin(4.5, 4.5, 4.5, 4.5)),
             legend.background = element_rect(fill = NA,
                                              color = NA),
             legend.key = element_rect(color = NA, fill = NA),
             #legend.key.width = unit(5, "lines"),
             #legend.spacing.x = unit(.05, "pt"),
             #legend.spacing.y = unit(.55, "pt"),
             #legend.margin = margin(0, 0, 10, 0),
             strip.text = element_text(face = "bold",
                                       margin = margin(b = 10)))

## theme settings for flipped plots
theme_flip <-
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_line(size = .6,
                                          color = "#eaeaea"))

## theme settings for maps
theme_map <- 
  theme_void(base_family = "Montserrat") +
  theme(legend.direction = "horizontal",
        legend.box = "horizontal",
        legend.margin = margin(10, 10, 10, 10),
        legend.title = element_text(size = 17, 
                                    face = "bold"),
        legend.text = element_text(color = "grey33",
                                   size = 12),
        plot.margin = margin(15, 5, 15, 5),
        plot.title = element_text(face = "bold",
                                  size = 20,
                                  hjust = .5,
                                  margin = margin(30, 0, 10, 0)),
        plot.subtitle = element_text(face = "bold",
                                     color = "grey33",
                                     size = 17,
                                     hjust = .5,
                                     margin = margin(10, 0, -30, 0)),
        plot.caption = element_text(size = 14,
                                    color = "grey33",
                                    hjust = .97,
                                    margin = margin(-30, 0, 0, 0)))

## numeric format for labels
num_format <- scales::format_format(big.mark = ",", small.mark = ",", scientific = F)

## main color backlinko
bl_col <- "#00d188"
bl_dark <- darken(bl_col, .3, space = "HLS")

## colors + labels for interval stripes
int_cols <- c("#bce2d5", "#79d8b6", bl_col, "#009f66", "#006c45", "#003925")
int_perc <- c("100%", "95%", "75%", "50%", "25%", "5%")

## colors for degrees (Bachelors, Massters, Doctorate in reverse order)
cols_degree <- c("#e64500", "#FFCC00", darken(bl_col, .1))

## gradient colors for position
colfunc <- colorRampPalette(c(bl_col, "#bce2d5"))
pos_cols <- colfunc(10)
```

# Read data

```{r}
df <- bind_rows(
    pmap_df(list(0:99), ~read_csv(glue("../proc_data/ahref/export_keywords_100_to_500/{.x}.csv"))) %>% 
        clean_names() %>% mutate(cat = "100-500"),
    pmap_df(list(0:99), ~read_csv(glue("../proc_data/ahref/export_keywords_500_to_1000/{.x}.csv"))) %>% 
        clean_names() %>% mutate(cat = "500-1000"),
    pmap_df(list(0:49), ~read_csv(glue("../proc_data/ahref/export_keywords_1000_to_10000/{.x}.csv"))) %>% 
        clean_names() %>% mutate(cat = "1000-10000"),
    pmap_df(list(0:33), ~read_csv(glue("../proc_data/ahref/export_keywords_10000_to_1000000000/{.x}.csv"))) %>% 
            clean_names() %>% mutate(cat = "10000+")
)

df %<>% mutate(
  difficulty_cat = case_when(
    difficulty <= 10 ~ "Easy",
    between(difficulty, 11, 30) ~ "Medium",
    between(difficulty, 31, 70) ~ "Hard",
    between(difficulty, 71, 100) ~ "Super hard"
  ))
  
dfs <- df %>% sample_n(20000) 

tibble("Number of rows" = format(df %>% nrow(), big.mark = ",")) %>% 
  pander()
```


<br>

# Preamble


<br>

The volume looks weird. It doesn't follow the initial categories:

```{r}
df %>% drop_na(volume) %>% 
    group_by(cat) %>% 
    summarise(
        n = n(),
        mean = mean(volume),
        median = median(volume),
        max = max(volume),
        min = min(volume)
        ) %>% 
    arrange(median) %>% 
    pander()
```

Let's look at some of the searches that had a low search volume in the initial data set:

```{r}
df %>% filter(cat == "100-500", volume > 10000) %>% 
    select(keyword, volume) %>% 
    head(5) %>% 
    pander()
```

This doesn't looks like low volume words. And indeed they were not in the original data sets for 100-500 volume. I'm not sure how they came in.

This brings up the issue of upscaling. 

For example, let's say we are interested in the average keyword difficulty. We could simply take the average keyword difficulty of all the keywords in these exported_keyword datasets. But the representation in this data set is skewed, so that the keywords with high search volume are vastly over-represented, compared to the list of words in the original data set. 

A more correct approach would be to weight them by how large a pool they are a selection from. Eg, if there are 100 keywords that are not included for each keyword in the 100-500 volume category, but only 1 keyword that was not included for each keyword in the 10000+ volume category, they would be assigned accordingly.

!!!D: I trust you on this on what makes more sense. 

In fact, let's see:

```{r}
length_keyword_files <- function(min, max){
  sql <- glue("SELECT count(*) as `count`
          FROM `dataforseo-bigquery.dataforseo_data.keyword_data` 
          WHERE location = 2840 
          AND keyword_info_search_volume >= {min}
          AND keyword_info_search_volume < {max}")
  tb <- bq_project_query("dataforseo-bigquery", sql)
  df <- bq_table_download(tb) %>% mutate(min = min, max = max)
}

scaling <- map2_df(c(100, 500, 1000, 10000), c(500, 1000, 10000, 1000000000), length_keyword_files) %>% 
    mutate(factor = count / 1000000) %>% relocate(min, max)

scaling %>% pander()
```

<br>

For now I will just use this list as if its truth and not adjust for volume. This can be changed later.

<br>


# Keyword difficulty


```{r}
tribble(~Mean, ~Median,
        round(mean(df$difficulty, na.rm = T), 2), median(df$difficulty, na.rm = T)) %>% 
  pander()

```


```{r difficulty_volume_scatter}
dfs %>%
  ggplot(aes(x = difficulty, y = volume)) +
  geom_jitter(size = 0.1, alpha = 0.1, height = 0.08, width = 0.3) +
  scale_y_log10(labels = comma) +
  geom_smooth(method='loess', formula= y~x) +
  labs(title = "Keyword difficulty and volume")
```

!!!D: Would be interested in the following finding: An increase by 100/500/1000 search volume leads to increase to a 0.5 difficulty score. Hence, may be it makes more sense to swap the the variables to make the difficulty a dependent variable. 



```{r difficulty_volume_violin}
dfs %>% drop_na(difficulty_cat) %>% 
  ggplot(aes(y = volume, x = difficulty_cat)) +
  geom_violin(draw_quantiles = c(0.5)) +
  scale_y_log10(labels = comma) +
  labs(x = "Difficulty category", title = "Keyword difficulty and volume")
```

!!!D: Please use the following keyword difficulty scales:

Easy: 0-10
Medium: 11-30
Hard: 31-70
Super hard: 71-100

Ranges should be displayed in the labels. 

People will most likely not understand a violin chart. Alternatives? box blot? 



```{r difficulty_cpc_scatter}
dfs %>%
  ggplot(aes(x = difficulty, y = cpc)) +
  geom_jitter(size = 0.1, alpha = 0.1, height = 0.08, width = 0.3) +
  scale_y_log10(labels = comma) +
  geom_smooth(method='loess', formula= y~x) +
  labs(title = "Keyword difficulty and cpc")
```

```{r difficulty_cpc_violin}
dfs %>% drop_na(difficulty_cat) %>% 
  ggplot(aes(y = cpc, x = difficulty_cat)) +
  geom_violin(draw_quantiles = c(0.5)) +
  scale_y_log10(labels = comma) +
  labs(x = "Difficulty category", title = "Keyword difficulty and cpc")
```

!!!D: similar comments as above. 

!!!D: Shame we cannot use the keyword categories here. May be we can try to solve this after the 3rd of November if time remains. Just curios how large the df would be if we select just the columns keyword and info_categories from the original data set. We could do on the google big query page to avoid that rstudio crashes (plus, apply some filters). Just curios to know: You probably have thought of running a left join but why is that not possible?  



<br>

# SERP features

```{r}
dff <- dfs %>% 
  select(keyword, volume, clicks, cpc, serp_features, cps) %>% 
  separate_rows(serp_features, sep = ",") %>% 
  mutate(serp_features = ifelse(is.na(serp_features), "(None)", serp_features))

nones <- dff %>% filter(serp_features == "(None)")

dffn <- dff %>% group_by(keyword) %>% 
  summarise(n_serp = n()) %>% 
  mutate(n_serp = ifelse(keyword %in% nones$keyword, 0, n_serp)) %>% 
  mutate(n_serp = ifelse(n_serp >= 6, "6+", as.character(n_serp))) %>% 
  mutate(n_serp = factor(n_serp, levels = c("0", "1", "2", "3", "4", "5", "6+")))

dffn <- left_join(dffn, dfs, by = "keyword")
```



```{r serp_presence, fig.height = 5, fig.width = 7}
dff %>% group_by(serp_features) %>% 
  summarise(prop = n() / nrow(dfs)) %>% 
  ggplot(aes(y = reorder(serp_features, prop), x = prop)) +
  geom_bar(stat = "identity", fill = "turquoise4", color = "black", width = 0.8) +
  scale_x_continuous(labels = scales::percent) +
  labs(y = "SERP feature", x = "", title = "Presence of SERP features")
```
```{r serp_presence_n}
dffn %>% group_by(n_serp) %>%
  summarise(n = n() / nrow(dffn)) %>% 
  ggplot(aes(x = n_serp, y = n)) +
  geom_bar(stat = "identity", fill = "turquoise4", color = "black", width = 0.8) +
  labs(x = "Number of serp features", y = "", title = "Distribution of SERP features") +
  scale_y_continuous(labels = scales::percent)
```


```{r serp_volume, fig.height = 5, fig.width = 7}
order <- dff %>% 
  group_by(serp_features) %>%
  summarise(volume = mean(volume, na.rm = T)) %>% 
  arrange(volume) %>% 
  pull(serp_features)


dff %>% 
  drop_na(serp_features) %>% 
  mutate(serp_features = factor(serp_features, levels = order)) %>% 
  ggplot(aes(y = serp_features, x = volume)) +
  stat_density_ridges(fill = "turquoise4", color = "black") +
  scale_x_log10(limits = c(10, 50000)) +
  labs(title = "SERP features and mean volume", x = "Mean volume")
```
```{r serp_volume_n}
dffn %>% group_by(n_serp) %>%
  summarise(volume = mean(volume, na.rm = T)) %>% 
  ggplot(aes(x = n_serp, y = volume)) +
  geom_bar(stat = "identity", fill = "turquoise4", color = "black", width = 0.8) +
  labs(x = "Number of serp features", title = "Number of SERP features and mean volume", y = "Mean volume")
```

```{r serp_volume_n_ridges}
dffn %>% 
  ggplot(aes(y = n_serp, x = volume)) +
  stat_density_ridges(fill = "turquoise4", color = "black") +
  scale_x_log10(labels = comma) +
  labs(y = "SERP features", title = "Number of SERP features and volume")
```



```{r sero_clicks}
order <- dff %>% 
  group_by(serp_features) %>%
  summarise(mean_clicks = mean(clicks, na.rm = T)) %>% 
  arrange(mean_clicks) %>% 
  pull(serp_features)


dff %>% 
  mutate(serp_features = factor(serp_features, levels = order)) %>% 
  mutate(clicks = clicks + 1) %>% 
  ggplot(aes(y = serp_features, x = clicks)) +
  stat_density_ridges(fill = "turquoise4", color = "black") +
  scale_x_log10(labels = comma)
```
```{r serp_clicks_n}
dffn %>% group_by(n_serp) %>%
  summarise(clicks = mean(clicks, na.rm = T)) %>% 
  ggplot(aes(x = n_serp, y = clicks)) +
  geom_bar(stat = "identity", fill = "turquoise4", color = "black", width = 0.8) +
  labs(x = "SERP features", title = "Number of SERP features and mean clicks", y = "Mean clicks")
```

```{r serp_clicks_n_ridge}
dffn %>% 
  mutate(clicks = clicks + 1) %>% 
  ggplot(aes(y = n_serp, x = clicks)) +
  stat_density_ridges(fill = "turquoise4", color = "black") +
  scale_x_log10(labels = comma) +
  labs(y = "SERP features", title = "Number of SERP features and clicks")
```


!!!D: Can we have a plot of the most often combinations? eg. https://tinyurl.com/y6b9lgva 

!!!D: Any interesting patterns with regards to keyword difficulty, or search eg. the higher the search and keyword difficulty the more SERP features?  Definition SERP feautres: A SERP feature is any result on a Google Search Engine Results Page (SERP) that is not a traditional organic result. The most common SERP Features are: Rich Snippets which add a visual layer to an existing result (e.g., review stars for product ratings).

!!!D: after the 3rd, may make sense to check if there is anything interesting on relationship between keyword category and SERP features. 
!!!D: Would be great to dive into clicks/CPS vs SERP features. I assume the clicks per search will be less with more SEERP features because people find an answer that Google already provides with their SERP features. 

Some definitions:

The Clicks column shows exactly how many times per month people tend to click any pages when googling this keyword. Some searches result in a lot of clicks, while other high search volume keywords may not bring in as much traffic from search due to the low number of clicks.

The keyword "chauffeur" has a high search volume of 67,000 searches per month. Yet that volume only resulted in 13,406 clicks. One probable reason could be that Google already gave what people wanted instantly - and there was no need to click on the search results.

!!!D: CPS column definition 

The CPS (Click per Search) shows an average number of clicks for all searches. It is basically a correlation between the Clicks metric and the Search Volume of the keyword. 

In the example given, people search for "wow chauffeur" less frequently than "chauffeur", yet the keyword has more Clicks than Searches. 

Further investigation reveals that the word "wow" actually stands for "World of Warcraft", and apparently, people are looking for information on how to summon a "chauffeur" in the game. That makes for a completely different search intent. 

And this is why we have the CPS metric. 

The higher the CPS (i.e people clicking on a few links to satisfy their search query) -- the more chances that you'll get some traffic even if you're not ranking #1 for that search query. 

More info: https://help.ahrefs.com/en/articles/624151-what-does-clicks-stand-for-in-keywords-explorer 


<br>

# Global volume

!!!D: That section is fine I would just clean up the labels/remove scientic notation. 

```{r}
dfv <- 
  bind_rows(
    df %>% mutate(region = "US"),
    df %>% mutate(volume = global_volume - volume, region = "International")
    )
```

International searches have much more total volume:

```{r}
dfv %>% group_by(region) %>% 
  summarise(volume = format(sum(volume, na.rm = T), big.mark = ",")) %>% 
  pander()
```

Internationally there are more searches with very low volume, while US has more searches with medium volume.

```{r comparison_count}
dfv %>% drop_na(volume) %>% 
  mutate(volume_group = case_when(volume < 100 ~ "< 100",
    between(volume, 100, 1000) ~ "100 - 1000",
    between(volume, 1000, 10000) ~ "1000 - 10,000",
    volume > 10000 ~ "10,000 +")) %>% 
  mutate(volume_group = factor(volume_group, levels = c("< 100", "100 - 1000", "1000 - 10,000", "10,000 +"))) %>% 
  group_by(volume_group, region) %>% 
  summarise(n = n()) %>% 
  ggplot(aes(x = volume_group, y = n, fill = region)) +
  geom_bar(stat = "identity", position = position_dodge(), width = 0.8)
```
There is not a large difference in the number of searches with very high volume. However, the total volume of these searches is a lot higher internationally

```{r comparison_volume, fig.width = 9}
dfv %>% drop_na(volume) %>% 
  mutate(volume_group = case_when(volume < 100 ~ "< 100",
    between(volume, 100, 1000) ~ "100 - 1000",
    between(volume, 1000, 10000) ~ "1000 - 10,000",
    between(volume, 10000, 100000) ~ "10,000 - 100,000",
    between(volume, 100000, 1000000) ~ "100,000 - 1M",
    volume > 1000000 ~ "1M +")) %>% 
  mutate(volume_group = factor(volume_group, levels = c("< 100", "100 - 1000", "1000 - 10,000", "10,000 - 100,000", "100,000 - 1M", "1M +"))) %>% 
  group_by(volume_group, region) %>% 
  summarise(n = sum(volume)) %>% 
  ggplot(aes(x = volume_group, y = n, fill = region)) +
  geom_bar(stat = "identity", position = position_dodge(), width = 0.8)
```

Looking at the number of searches with above 1 million volume:

```{r}
df_int <- df %>% mutate(international_volume = global_volume - volume) %>% 
  filter(international_volume > 0, global_volume > 0) %>% 
  mutate(volume_diff = log10(international_volume) - log10(volume))

tibble(International = df_int %>% filter(international_volume > 1000000) %>% nrow(),
       US = df_int %>% filter(volume > 1000000) %>% nrow()) %>% 
  pander()
```


```{r international_v_us_volume}
df_int_s <- df_int %>% sample_n(200000)

df_int_s %>% 
  ggplot(aes(x = volume, y = international_volume)) +
  geom_jitter(size = 0.05, alpha = 0.02, height = 0.15, width = 0.15) +
  scale_x_log10(labels = comma, expand = c(0,0)) +
  scale_y_log10(labels = comma, expand = c(0,0)) +
  geom_abline(intercept = 0, slope = 1, color = "turquoise4", size = 1) +
  labs(x = "US volume", y = "International volume")
```

<br>

We can see that they mostly follow each other, but there are some searches with large difference between them.

Higher volume internationally:

```{r}
df_int %>% 
  arrange(desc(volume_diff)) %>% 
  filter(volume != 60) %>% 
  select(keyword, us_volume = volume, international_volume) %>% 
  head(5) %>% 
  pander()
```

<br>

Higher volume in US:

```{r}
df_int %>% 
  arrange(volume_diff) %>% 
  select(keyword, us_volume = volume, international_volume) %>% 
  head(5) %>% 
  pander()
```

<br>


Searches that have higher volume in US have a higher click-per-search on average than searches that have higher volume internationally.

```{r international_cps}
df_int_s %>% 
  ggplot(aes(x = volume_diff, y = cps)) +
  geom_point(alpha = 0.08, size = 0.08) +
  #scale_y_log10(labels = comma) +
  geom_smooth(method='lm', formula= y~x) +
  scale_x_continuous(breaks = c(-2, 0, 3), labels = c("More US", "0", "More international")) +
  labs(x = "")
```
<br>

They also have a higher cost-per-click on average

```{r international_cpc}
df_int_s %>% 
  ggplot(aes(x = volume_diff, y = cpc)) +
  geom_point(alpha = 0.08, size = 0.08) +
  scale_y_log10(labels = comma) +
  geom_smooth(method='lm', formula= y~x) +
  scale_x_continuous(breaks = c(-2, 0, 3), labels = c("More US", "0", "More international")) +
  labs(x = "")
```
<br>

Searches that have higher volume internationally, tend to have higher difficulty

```{r international_difficulty}
df_int_s %>% 
  ggplot(aes(x = volume_diff, y = difficulty)) +
  geom_point(alpha = 0.08, size = 0.08) +
  #scale_y_log10(labels = comma) +
  geom_smooth(method='lm', formula= y~x) +
  scale_x_continuous(breaks = c(-2, 0, 3), labels = c("More US", "0", "More international")) +
  labs(x = "")
```

<br>

# Clicks


```{r}
tribble(~Mean, ~Median,
        round(mean(df$clicks, na.rm = T), 2), median(df$clicks, na.rm = T)) %>% 
  pander()

```
```{r}
dfs %>% ggplot(aes(x = clicks)) +
  geom_histogram(fill = "turquoise4", color = "black") +
  scale_x_log10(labels = comma) +
  labs(title = "Distribution of number of clicks per search", y = "", x = "")
```

!!!J: I don't think there is any data in the file about organic / paid?
!!!D: No, there isn´t. We just have CPC. May be we can dive a bit into CPS. 

Can we get a vertical line with the mean in the chart? Like so: https://tinyurl.com/y4r3kvns


!!!D: Clicks and Clicks per Volume (CPS) are two different things. See https://help.ahrefs.com/en/articles/624151-what-does-clicks-stand-for-in-keywords-explorer  


# Return Rate

May be something interesting here?

Return Rate (RR)
Return Rate (RR) shows how often the same person searches for a given keyword over a 30-day period.

RR1 means that people typically don’t search for that keyword again within 30 days.

But RR2 and RR3 don’t mean that people search for a given keyword two and three times per month respectively. It just means that the second keyword tends to get more repeated searches than the first one.

https://ahrefs.com/blog/seo-metrics/#:~:text=Return%20Rate%20(RR)%20shows%20how,three%20times%20per%20month%20respectively. 

